---
title: "SPiCT assessment model for {{STOCK_NAME}} (ICES areas {{ICES_AREAS}})"
subtitle: "Working document for the {{WORKING_GROUP}} {{ASSESSMENT_YEAR}}"
date: today
published-title: "Version"
params:
  assessment_year: 2026       # Current assessment year
  advice_year: 2027           # Year for which advice is given
  prev_advice_year: 2024      # Year advice was last given
  run_retro_chunk: TRUE       # Whether to run the retrospective analysis chunk
  nretroyears: 5              # Number of years to peel in retrospective analysis
  nhindcastyears: 5           # Number of years for hindcast evaluation
  load_from_files: FALSE      # Load pre-saved model/management objects instead of fitting (requires prior run with save_large_files = TRUE)
format:
  html:
    self-contained: true
    fig-width: 9
    fig-height: 6
    code-fold: true
    toc: true
    toc-depth: 2
    output-file: "{{STOCK_NAME}} assessment model"
  pdf:
    fig-width: 7
    fig-height: 5
    toc: true
    toc-depth: 2
    output-file: "{{STOCK_NAME}} assessment model"
    knitr:
      opts_chunk:
        echo: false
    include-in-header:
      text: |
        \usepackage{booktabs}
        \usepackage{longtable}
        \usepackage{array}
        \usepackage{multirow}
        \renewcommand{\arraystretch}{1.1}
        \small
bibliography: src/documents/zotero_library.bib
csl: src/documents/ices_jms.csl
execute:
  message: false
  warning: false
editor_options:
  chunk_output_type: console
---

# Introduction

::: {.callout-warning}
## Exploratory assessment — not official advice

This is an **exploratory** SPiCT (Surplus Production model in Continuous Time) assessment of beaked redfish (*Sebastes mentella*) in ICES areas 1 and 2. It is **not official JRN-AFWG advice** and should not be used as such. The official Joint Russian-Norwegian Working Group on Arctic Fisheries (JRN-AFWG) stock assessment for beaked redfish is conducted with the gadget3 age-structured model (<https://gadget-framework.github.io/>). This document is a supplementary analysis exploring the suitability and outputs of a surplus-production modelling approach.

All prior values are currently **placeholders** from the golden redfish SPiCT model. They should be replaced by alternatives adjusted for beaked redfish.
:::

This document compiles a SPiCT (Surplus Production model in Continuous Time) assessment [@pedersen2017] for Northeast Arctic [beaked redfish](https://www.hi.no/hi/temasider/arter/uer/snabeluer) (*Sebastes mentella*) in ICES areas 1 and 2, and constitutes a transparent working document for the Joint Russian-Norwegian Working Group on Arctic Fisheries (JRN-AFWG) `r params$assessment_year` assessment. The document is compiled using Quarto, the next-generation publishing system from Posit (formerly RStudio). `r if(knitr::is_html_output()) paste("The code has been hidden by default but can be expanded using the arrow buttons.") else paste("The HTML version of this document is more readable and contains code for reproducibility.")`

Beaked redfish is a long-lived, slow-growing scorpaenid inhabiting the Norwegian and Barents Seas, and adjacent shelf waters. The stock is assessed by JRN-AFWG within ICES subareas 1 and 2.

# Data and model setup

```{r setup, include=FALSE}
source("src/0_setup.R")
source("src/spict_functions.R")
source("src/ices_plots.R")
source("src/make_table.R")

if (exists("params")) {
  assessment_year <- params$assessment_year
  advice_year <- params$advice_year
  prev_advice_year <- params$prev_advice_year
  model_name <- paste0("{{STOCK_NAME_LOWER_SNAKE}}_spict_", assessment_year)
  nretroyears <- params$nretroyears
  nhindcastyears <- params$nhindcastyears
} else {
  model_name <- "{{STOCK_NAME_LOWER_SNAKE}}_spict_{{ASSESSMENT_YEAR}}"
  nretroyears <- 5
  nhindcastyears <- 5
}

save_large_files <- FALSE
save_summary <- TRUE
load_from_files <- if (exists("params")) params$load_from_files else FALSE
index_name <- "Over 30 cm biomass index"

# PLACEHOLDER: Set to catch reporting quality breakpoints for beaked redfish.
# Golden redfish uses 1987 (AFWG start correcting catches) and 2022 (Norwegian
# sales-note trust threshold). Replace with JRN-AFWG equivalent breakpoints.
stdev_high_year <- 1987
stdev_low_year <- 2022
stdev_high_val <- 3 # catch uncertainty multiplier before stdev_high_year
```

```{r data-preparation}
if (FALSE) {
  # Switch to update the catch data
  source("src/1_process_catches.R")
}

catches <- read.csv("data/catches/{{STOCK_NAME}}_catches_for_SPiCT.csv") |>
  as_tibble() |>
  rename_with(tolower) |>
  dplyr::select(-hist)

catch_totals_match <- catches |>
  filter(!is.na(nor)) |>
  rowwise() |>
  mutate(total2 = sum(c_across(c("nor", "rus", "int")), na.rm = TRUE)) |>
  mutate(equal = round(total2) == round(total)) |>
  pull(equal) |>
  all()

if (!catch_totals_match) {
  stop(
    "Catch totals do NOT match the sum of the components. Please check the data."
  )
}

last_data_year <- max(catches$year, na.rm = TRUE)
first_catch_year <- min(catches$year, na.rm = TRUE)
if (!exists("params")) {
  assessment_year <- last_data_year + 1
  advice_year <- last_data_year + 2
}
intermediate_year <- assessment_year

index <- read_rds("data/indices/{{STOCK_CODE}}-assessment-survey-indices.rds")[[2]] |>
  mutate(
    index = est / mean(est, na.rm = TRUE),
    index_lwr = lwr / mean(est, na.rm = TRUE),
    index_upr = upr / mean(est, na.rm = TRUE),
    stdevI = se / mean(se, na.rm = TRUE)
  )

first_index_year <- min(index$year, na.rm = TRUE)
first_data_year <- min(first_catch_year, first_index_year)

input_spict <- list(
  timeC = catches$year,
  obsC = catches$total,
  timeI = index$year + (6 / 12), # index timing during the year (June)
  obsI = index$index
)

input_spict$phases$logn <- -1
input_spict$ini$logn <- log(2)

# PLACEHOLDER: priors are golden redfish values. Update from beaked redfish
# life-history parameters or JRN-AFWG literature before a real assessment.
r_priors <- list(
  logbkfrac = c(log(0.9), 0.5, 1),
  logr = c(log(0.064), 0.5, 1),
  logsdb = c(log(0.05), 0.2, 1),
  logalpha = c(0, 0, 0),
  logbeta = c(0, 0, 0)
)

# PLACEHOLDER: catch uncertainty ramp breakpoints are golden redfish values.
# Set stdev_high_year and stdev_low_year in the setup chunk to beaked redfish
# reporting quality breakpoints before a real assessment.
r_sdfacs <- list(
  stdevfacC = data.frame(year = min(catches$year):max(catches$year)) |>
    mutate(
      uncertainty = case_when(
        year < stdev_high_year ~ stdev_high_val,
        year > stdev_low_year ~ 1,
        .default = NA_real_
      )
    ) |>
    mutate(uncertainty = zoo::na.approx(uncertainty)) |>
    mutate(stdevfacC = uncertainty / mean(uncertainty, na.rm = TRUE)) |>
    pull(stdevfacC),
  stdevfacI = index$stdevI
)

inp <- check.inp(input_spict, verbose = TRUE)

for (nm in names(r_priors)) {
  inp$priors[[nm]] <- r_priors[[nm]]
}

inp$stdevfacC <- r_sdfacs$stdevfacC
inp$stdevfacI <- r_sdfacs$stdevfacI

settings_tbl <- tibble(
  setting = c(
    "Stock",
    "Catch years",
    "Catch units",
    "Survey index",
    "Survey timing in SPiCT",
    "Index scaling",
    "Shape parameter n",
    "Deviations priors",
    "Catch uncertainty scaling"
  ),
  value = c(
    "Northeast Arctic beaked redfish, ICES areas 1 and 2",
    paste(min(catches$year), "to", max(catches$year)),
    "Tonnes",
    paste0(index_name, " (", min(index$year), " to ", max(index$year), ")"),
    "June (year + 6/12)",
    "Survey estimates divided by their mean",
    ifelse(
      input_spict$ini$logn == log(2),
      "Schaefer model (log(2)) [PLACEHOLDER]",
      paste0("Estimated, ", input_spict$ini$logn)
    ),
    "logalpha and logbeta deactivated [PLACEHOLDER]",
    paste0(
      "Linear ramp from ",
      stdev_high_val,
      "x before ",
      stdev_high_year,
      " to 1 after ",
      stdev_low_year,
      ", then normalized to mean 1 [PLACEHOLDER]"
    )
  )
)
```

Catch data extend through `r last_data_year`, so this document is framed as the `r assessment_year` assessment with forecast calculations for `r advice_year`.

The model is configured as a Schaefer surplus-production model with the shape parameter $n$ fixed at $\log(2)$. A prior constraining a low initial depletion (`logbkfrac`) is used assuming a long unfished period before the modern fishery. The prior on intrinsic growth rate (`logr`) is a placeholder from golden redfish; replace with a beaked redfish estimate from FishLife or JRN-AFWG literature. The process variance prior (`logsdb`) constrains unrealistically smooth biomass trajectories. The coupling parameters `logalpha` and `logbeta` are deactivated so that the two error structures are estimated independently.

Catch observations before `r stdev_high_year` are downweighted using a linearly interpolated standard-deviation multiplier that decreases from `r stdev_high_val`× (pre-`r stdev_high_year`) to 1× (post-`r stdev_low_year`); these breakpoints are **placeholders** and should be set to beaked redfish reporting quality breakpoints.

```{r tbl-settings}
make_table(
  settings_tbl,
  caption = "Model configuration used in this assessment document. Rows marked [PLACEHOLDER] require updating with beaked redfish–specific values."
)
```

## Catch history

```{r fig-catch-history}
#| fig-cap: Reported catches of Northeast Arctic beaked redfish in ICES areas 1 and 2.
#| fig-height: 4
catches |>
  mutate(total = ifelse(!is.na(nor), NA_real_, total)) |>
  pivot_longer(-year) |>
  mutate(
    name = recode_factor(
      name,
      total = "Total",
      nor = "Norway",
      rus = "Russia",
      int = "Other"
    ),
    value = value / 1000
  ) |>
  ggplot(aes(year, value, fill = name)) +
  geom_col() +
  scale_fill_manual(values = cols) +
  scale_x_continuous(
    breaks = seq(1915, last_data_year, 10),
    expand = expansion(c(0.01))
  ) +
  scale_y_continuous(expand = expansion(c(0, 0.02)), n.breaks = 10) +
  labs(x = "Year", y = "Catch (kt)", fill = NULL) +
  theme(
    panel.grid.major.y = element_line(color = "grey80", size = 0.2),
    panel.grid.minor.y = element_line(color = "grey90", size = 0.1)
  )
```

The catch time series begins in 1952 and spans more than seven decades. Catches peaked in `r catches$year[[which.max(catches$total)]]` at approximately `r round(max(catches$total),-3)/1e3` kt. Following this peak, catches declined sharply through the late 1970s and 1980s and continued falling through the 1990s. Historic lows of around `r round(min(catches$total),-2)/1e3` kt were recorded in `r catches$year[[which.min(catches$total)]]` due to moratorium following a poor recruitment period. From approximately 2014, catches increased again. Recent catches (2020–2025) have ranged between `r catches |> filter(year %in% 2020:assessment_year) |> pull(total)  |> range() |> round(-3) |> (\(x) x / 1e3)() |> list_values()` kt, with Norway accounting for the largest share. The pre-`r stdev_high_year` catches carry greater uncertainty and are downweighted accordingly in the model.

## SPiCT input data

```{r fig-spict-input}
#| fig-cap: Catch series and the survey index used as SPiCT input. Catches use the left axis and the scaled survey index uses the right axis. 
#| fig-height: 4
y_max <- max(catches$total, na.rm = TRUE)
index_lo <- floor(min(index$index, na.rm = TRUE) * 10) / 10
index_hi <- ceiling(max(index$index, na.rm = TRUE) * 10) / 10
scale_factor <- y_max / (index_hi - index_lo)

index_plot <- index |>
  transmute(
    time = year + (6 / 12),
    index = index,
    scaled_index = (index - index_lo) * scale_factor
  )

ggplot() +
  geom_col(
    data = catches,
    aes(year, total),
    fill = "grey75",
    color = "grey60"
  ) +
  geom_line(
    data = index_plot,
    aes(time, scaled_index),
    color = cols[2],
    linewidth = 1
  ) +
  scale_x_continuous(
    breaks = seq(1910, last_data_year, 5),
    expand = expansion(mult = c(0, 0.01))
  ) +
  scale_y_continuous(
    name = "Catch (t)",
    expand = expansion(mult = c(0, 0.05)),
    sec.axis = sec_axis(
      ~ . / scale_factor + index_lo,
      name = "Survey index (relative)"
    )
  ) +
  labs(x = "Year")
```

The survey index covers `r min(index$year)`–`r max(index$year)`. 

```{r fig-prior-overview}
#| fig-cap: Catch and survey overview together with diagnostic plots used to judge whether the SPiCT assumptions are broadly reasonable before fitting the model.
#| fig-height: 8
plotspict.ci(inp)
```

# Model fitting

The model was fitted using `fit.spict()` with increased iteration limits to ensure convergence. One-step-ahead (OSA) residuals and process residuals were calculated for diagnostic purposes, and sensitivity to initial values was assessed using `check.ini()`.

```{r fit-model, results='hide'}
model_path <- file.path(
  "data",
  "model_output",
  "saved_models",
  paste0("res_", model_name, ".rds")
)

if (load_from_files) {
  if (!file.exists(model_path)) {
    stop(
      "Model file not found: ",
      model_path,
      "\nRun with load_from_files = FALSE and save_large_files = TRUE first."
    )
  }
  fit <- readRDS(model_path)
} else {
  inp$optimiser.control <- list(iter.max = 1e5, eval.max = 1e5)
  fit <- fit.spict(inp)
  fit <- calc.osa.resid(fit)
  fit <- calc.process.resid(fit)
  fit <- check.ini(fit)
}
```

```{r convergence-check}
#| results: asis
conv <- fit$opt$convergence
sd_ok <- all(is.finite(fit$sd))
if (conv == 0 && sd_ok) {
  cat(
    "> **Convergence:** The model converged normally",
    "(optimizer exit code 0; all standard errors are finite).\n"
  )
} else {
  msgs <- c()
  if (conv != 0) {
    msgs <- c(msgs, paste0("optimizer exit code ", conv))
  }
  if (!sd_ok) {
    msgs <- c(msgs, "non-finite standard errors detected")
  }
  cat("> **WARNING:** Convergence issue —", paste(msgs, collapse = "; "), "\n")
}
```

# Results

Full model output from `summary(fit)` is available in the collapsible code block below.

```{r model-output, collapse=TRUE}
summary(fit)
```

## Parameter estimates

```{r tbl-parameter-estimates}
fmt_val <- function(x) {
  dplyr::case_when(
    is.na(x) ~ NA_character_,
    abs(x) > 1e3 ~ formatC(x, digits = 0, format = "f"),
    abs(x) > 10 ~ formatC(x, digits = 1, format = "f"),
    abs(x) > 1 ~ formatC(x, digits = 3, format = "f"),
    abs(x) >= 1e-3 ~ formatC(x, digits = 4, format = "f"),
    TRUE ~ formatC(x, digits = 3, format = "e")
  )
}

parameter_tbl <- sumspict.parest(fit) |>
  as.data.frame() |>
  tibble::rownames_to_column("parameter") |>
  dplyr::mutate(dplyr::across(where(is.numeric), fmt_val))

make_table(parameter_tbl, caption = "Estimated SPiCT parameters.")
```

Parameter estimates are given on the natural scale with 95% confidence intervals. Key parameters to check are the intrinsic growth rate $r$, the carrying capacity $K$, the initial depletion fraction $B/K$, and the process and observation error standard deviations.

## Deterministic reference points

```{r tbl-deterministic-reference-points}
dref_tbl <- sumspict.drefpoints(fit) |>
  as.data.frame() |>
  tibble::rownames_to_column("reference_point") |>
  dplyr::mutate(dplyr::across(where(is.numeric), fmt_val))

make_table(
  dref_tbl,
  caption = "Deterministic reference points from the fitted model."
)
```

## Stochastic reference points

```{r tbl-stochastic-reference-points}
sref_tbl <- sumspict.srefpoints(fit) |>
  as.data.frame() |>
  tibble::rownames_to_column("reference_point") |>
  dplyr::mutate(dplyr::across(where(is.numeric), fmt_val))

make_table(
  sref_tbl,
  caption = "Stochastic reference points from the fitted model."
)
```

## Current stock status

```{r tbl-stock-status}
states_tbl <- sumspict.states(fit) |>
  as.data.frame() |>
  tibble::rownames_to_column("quantity") |>
  dplyr::mutate(dplyr::across(where(is.numeric), fmt_val))

make_table(
  states_tbl,
  caption = paste0(
    "Estimated stock status at the end of the assessment period (",
    last_data_year,
    ")."
  )
)
```

```{r stock-status-inline, results='asis'}
#| include: true
tryCatch(
  {
    st <- sumspict.states(fit)
    bbmsy <- st["BBmsy/MSYBtrigger", "est"]
    ffmsy <- st["FFmsy", "est"]
    status_b <- if (bbmsy >= 1) "above" else "below"
    status_f <- if (ffmsy <= 1) "at or below" else "above"
    cat(sprintf(
      "\nAt the end of %d, biomass is estimated to be **%s $B_{MSY}$ trigger** ($B/B_{MSY\\ trigger}$ = %.2f) and fishing mortality is **%s $F_{MSY}$** ($F/F_{MSY}$ = %.2f).\n",
      last_data_year,
      status_b,
      bbmsy,
      status_f,
      ffmsy
    ))
  },
  error = function(e) invisible(NULL)
)
```

## General model overview

```{r fig-model-overview}
#| fig-cap: Standard SPiCT overview plot showing the fitted biomass trajectory, fishing mortality, catch, and survey index with 95% confidence intervals.
#| fig-height: 10
plot(fit)
```

## Relative biomass and fishing mortality

```{r fig-bbmsy}
#| fig-cap: Estimated biomass relative to the MSY B~trigger~ (B/B~MSY~). The horizontal dashed line at 1 indicates the trigger reference point.
plotspict.bbmsy(fit)
```

```{r fig-ffmsy}
#| fig-cap: Estimated fishing mortality relative to F~MSY~. The horizontal dashed line at 1 indicates F~MSY~.
plotspict.ffmsy(fit)
```

## Kobe plot

```{r fig-kobe}
#| fig-cap: Kobe plot showing the estimated trajectory of stock status in B/B~MSY~–F/F~MSY~ space. The current year estimate is highlighted. Green quadrant indicates the stock is above B~MSY~ trigger and F is below F~MSY~.
plotspict.fb(fit)
```

# Diagnostics

Model diagnostics evaluate: (1) whether the model converged to a unique maximum; (2) the pattern and distribution of residuals; and (3) whether the data are informative relative to the priors.

## Sensitivity to initial values

```{r tbl-sensi-initial-values}
ini_sensi_tbl <- fit$check.ini$resmat |>
  as.data.frame() |>
  tibble::rownames_to_column("Run") |>
  dplyr::mutate(dplyr::across(where(is.numeric), fmt_val))

make_table(
  ini_sensi_tbl,
  caption = "Sensitivity of parameter estimates to different initial values. Small variation across runs indicates a robust optimum."
)
```

## OSA residuals

```{r fig-osa-diagnostics}
#| fig-cap: One-step-ahead (OSA) residual diagnostics. The four panels show (top-left) residuals over time, (top-right) residual autocorrelation, (bottom-left) a QQ plot against a normal distribution, and (bottom-right) a cumulative sum test.
#| fig-height: 10
plotspict.diagnostic(fit)
```

## Process residuals

```{r fig-process-diagnostics}
#| fig-cap: Process residual diagnostics for the fitted model.
#| fig-height: 10
plotspict.diagnostic.process(fit)
```

## Priors vs posteriors

```{r fig-priors-posteriors}
#| fig-cap: Prior (dashed) and posterior (solid) distributions for each estimated parameter.
plotspict.priors(fit)
```

# Retrospective analysis and hindcasting

Retrospective analysis evaluates model stability by sequentially removing the most recent years of data and refitting the model. Consistent over- or underestimation of $B/B_{MSY}$ across peels (quantified by Mohn's $\rho$) is an indicator of retrospective bias. A common rule of thumb is that $|\rho| > 0.20$ warrants investigation.

```{r retros, eval=params$run_retro_chunk && !load_from_files}
tryCatch(
  {
    fit <- retro(fit, nretroyear = nretroyears, mc.cores = 1)
  },
  error = function(e) {
    message("Retro did not compile: ", e$message)
  }
)
```

```{r mohns-rho, eval=params$run_retro_chunk, results='asis'}
tryCatch(
  {
    rho_b <- mohns.rho(fit, what = "BBmsy")
    rho_f <- mohns.rho(fit, what = "FFmsy")
    cat(sprintf(
      "\nMohn's $\\rho$: $B/B_{MSY}$ = **%.3f**, $F/F_{MSY}$ = **%.3f**.\n",
      rho_b,
      rho_f
    ))
  },
  error = function(e) invisible(NULL)
)
```

```{r fig-retrospective-bbmsy, eval=params$run_retro_chunk}
#| fig-cap: Retrospective analysis of biomass relative to B~MSY~. Each line represents a different peel; the black line is the full-data fit.
#| fig-height: 8
plotspict.retro(fit)
```

```{r fig-retrospective-bbmsy-parameters, eval=params$run_retro_chunk}
#| fig-cap: Parameter estimates across retrospective peels.
#| fig-height: 8
plotspict.retro.fixed(fit)
```

```{r fig-hindcast, eval=params$run_retro_chunk}
#| fig-cap: Hindcast evaluation showing the model's ability to predict withheld observations.
tryCatch(
  {
    if (!load_from_files) {
      fit <- hindcast(fit, npeels = nhindcastyears)
      if (save_large_files) {
        dir.create(dirname(model_path), recursive = TRUE, showWarnings = FALSE)
        saveRDS(fit, file = model_path, compress = "xz")
      }
    }
    plotspict.hindcast(fit)
  },
  error = function(e) {
    message("Hindcast skipped: ", e$message)
  }
)
```

# Management scenarios

Four standard management scenarios are evaluated for `r advice_year`: (1) **currentF** — catches continue at the current fishing mortality; (2) **Fmsy** — catches are set to achieve $F_{MSY}$; (3) **noF** — no fishing (stock recovery trajectory); (4) **ices** — the ICES MSY advice rule (harvest control rule with $B_{trigger}$ at $0.5 \times B_{MSY}$ and $B_{lim}$ at $0.3 \times B_{MSY}$, using the 35th percentile). Risk probabilities are the probability that $B$ falls below $0.5 \times B_{MSY}$ or that $F$ exceeds $F_{lim}$.

```{r management-scenarios}
mgmt_path <- file.path(
  "data",
  "model_output",
  "saved_models",
  paste0("mgmt_", model_name, ".rds")
)

if (load_from_files) {
  if (!file.exists(mgmt_path)) {
    stop(
      "Management file not found: ",
      mgmt_path,
      "\nRun with load_from_files = FALSE and save_large_files = TRUE first."
    )
  }
  management <- readRDS(mgmt_path)
} else {
  management <- manage(
    fit,
    scenarios = c("currentF", "Fmsy", "noF", "ices"),
    maninterval = c(advice_year, advice_year + 1),
    maneval = advice_year + 1,
    verbose = FALSE
  )
  if (save_large_files) {
    dir.create(dirname(mgmt_path), recursive = TRUE, showWarnings = FALSE)
    saveRDS(management, file = mgmt_path, compress = "xz")
  }
}

manOutput <- sumspict.manage(management, include.unc = TRUE)

management_tbl <- manOutput$est |>
  as.data.frame() |>
  tibble::rownames_to_column("scenario") |>
  dplyr::mutate(dplyr::across(where(is.numeric), fmt_val))

risk <- spictRisk(
  management,
  bmsyfrac = 0.5,
  years = c(advice_year - 1, advice_year)
)

manTable <- bind_cols(
  manOutput$est,
  manOutput$unc,
  risk %>%
    mutate(across(BbelowBmsy:FaboveFlim, ~ . * 100)) %>%
    pivot_wider(
      id_cols = Scenario,
      values_from = BbelowBmsy:FaboveFlim,
      names_from = Year
    )
) %>%
  mutate(Scenario = rownames(manOutput$est)) %>%
  relocate(Scenario)

make_table(
  management_tbl,
  caption = paste("Management scenario point estimates for", advice_year, ".")
)
```

```{r fig-management-scenarios}
#| fig-cap: Harvest control rule and management scenario projections.
plotspict.hcr(management)
```

# SPiCT summary

```{r save-summary, include=FALSE}
tryCatch(
  {
    spict_summary <- list(
      summary = data.frame(
        year = as.numeric(row.names(get.par("logBBmsy", fit, exp = TRUE))),
        BBmsy = as.data.frame(get.par("logBBmsy", fit, exp = FALSE)),
        FFmsy = as.data.frame(get.par("logFFmsy", fit, exp = FALSE)),
        K = as.data.frame(get.par("logK", fit, exp = FALSE)),
        r = as.data.frame(get.par("logr", fit, exp = FALSE)),
        n = as.data.frame(get.par("logn", fit, exp = FALSE)),
        sdi1 = as.data.frame(get.par("logsdi", fit, exp = FALSE))[1, ],
        sdi2 = as.data.frame(get.par("logsdi", fit, exp = FALSE))[2, ],
        sdc = as.data.frame(get.par("logsdc", fit, exp = FALSE)),
        BKfrac = as.data.frame(get.par("logbkfrac", fit, exp = FALSE))
      ) %>%
        left_join(data.frame(year = inp$timeC, total_catch = inp$obsC)) %>%
        full_join(data.frame(
          year = min(management$inp$timeC):management$inp$timepredc,
          Catch_pred = as.data.frame(get.par("logCpred", fit, exp = TRUE))
        )) %>%
        full_join(data.frame(year = inp$timeI[[1]], index = inp$obsI[[1]])),
      refpoints = sumspict.drefpoints(fit),
      state = sumspict.states(fit),
      pars = as.data.frame(sumspict.parest(fit)),
      manTable = manTable,
      priors = fit$inp$priors,
      assessment_year = assessment_year,
      tac_year = advice_year
    )
  },
  error = function(e) {
    message("\n An error occurred in the SPiCT summary chunk:\n", e$message)
  }
)

if (save_summary && !load_from_files) {
  tryCatch(
    {
      dest <- paste0(
        "data/model_output/spict_summaries/",
        "sum_",
        model_name,
        ".rds"
      )
      if (!dir.exists(dirname(dest))) {
        dir.create(dirname(dest), recursive = TRUE)
      }
      saveRDS(spict_summary, file = dest, compress = "xz")
    },
    error = function(e) {
      message("\n An error occurred in the SPiCT summary chunk:\n", e$message)
    }
  )
}
```

```{r fig-summary-plot}
#| fig-cap: "ICES assessment summary plot showing catch, B/BMSY, and F/FMSY trajectories."
tryCatch(
  {
    summary_plot(spict_summary)
  },
  error = function(e) {
    message("\n An error occurred in the ICES summary plot chunk:\n", e$message)
  }
)
```

# References

::: {#refs}
:::

# Session information

<details>
<summary>R package versions and system information</summary>
```{r session-info}
#| echo: true
sessionInfo()
```
</details>
