---
title: ""
subtitle: ""
format:
  docx:
    # advice_template.docx is a styles-only Quarto reference-doc (heading,
    # table and body styles plus page setup; no document content). Replace it
    # with the working group's own Word template when one is available.
    reference-doc: src/documents/advice_template.docx
    number-sections: false
    fig-width: 6.5
    fig-height: 4
    fig-dpi: 300
    fig-align: left
  # html:
  #   embed-resources: true
  #   css: src/documents/ices_advice.css
  #   toc: true
  #   toc-depth: 1
  #   toc-title: "Contents"
  #   fig-width: 7
  #   fig-height: 4
  #   fig-dpi: 150
crossref:
  fig-title: '**Figure**'
  tbl-title: '**Table**'
  title-delim: '**:**'
bibliography: src/documents/zotero_library.bib
# TODO: Replace nocite references with JRN-AFWG beaked redfish sources.
# The references below are golden redfish / ICES AFWG placeholders.
nocite: |
  @ices-cat-1-2
  @ices2023c
  @ices2026-afwg
csl: src/documents/ices_jms.csl
execute:
  echo: false
  warning: false
  message: false
editor_options:
  chunk_output_type: console
output-file: "{{STOCK_NAME}} advice sheet"
params:
  assessment_year: 2026
  advice_year: 2027
  prev_advice: 0 # previous advice in tonnes
---

```{r setup}
#| include: false
source("src/0_setup.R")

extra_pkgs <- c(
  "officedown",
  "officer",
  "flextable",
  "icesAdvice",
  "cowplot",
  "xml2",
  "kableExtra"
)
to_install <- extra_pkgs[!extra_pkgs %in% rownames(installed.packages())]
if (length(to_install)) {
  install.packages(to_install)
}
invisible(lapply(extra_pkgs, function(p) {
  suppressPackageStartupMessages(library(p, character.only = TRUE))
}))

page_width_in <- 6.7

source("src/ices_plots.R")

if (isTRUE(knitr::opts_knit$get("rmarkdown.pandoc.to") == "docx")) {
  knitr::opts_chunk$set(out.width = "6.3in")
}

set_flextable_defaults(
  font.family = "Calibri",
  font.size = 9,
  table.layout = "fixed",
  border.color = "black",
  background.color = "white",
  big.mark = " ",
  decimal.mark = ".",
  padding = 2
)

fit_ft_page <- function(ft, max_width = page_width_in) {
  col_widths <- ft$body$colwidths
  total <- sum(col_widths)
  if (length(total) == 1 && is.finite(total) && total > 0) {
    scale <- max_width / total
    ft <- flextable::width(
      ft,
      j = seq_along(col_widths),
      width = col_widths * scale
    )
  }
  flextable::set_table_properties(ft, layout = "fixed", width = 1)
}

ices_ft <- function(ft) {
  ft |>
    bg(bg = "#E8EAEA", part = "header") |>
    border_inner(fp_border(color = "black", width = 0.5)) |>
    border_outer(fp_border(color = "black", width = 0.75)) |>
    font(fontname = "Calibri", part = "all") |>
    fontsize(size = 9, part = "all") |>
    align(align = "center", part = "header") |>
    padding(padding = 2, part = "all") |>
    autofit() |>
    fit_ft_page()
}

ices_theme <- theme_bw(8) +
  theme(
    axis.title.y = element_text(face = "bold"),
    axis.title.x = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    panel.grid.minor.y = element_blank(),
    strip.background = element_blank(),
    panel.background = element_blank(),
    plot.background = element_blank(),
    legend.background = element_blank(),
    legend.box.background = element_blank(),
    plot.margin = margin(t = 3, r = 5, b = 3, l = 3, unit = "pt")
  )

theme_set(ices_theme)
```

```{r data}
if (!exists("params")) {
  params <- list(assessment_year = 2026, advice_year = 2027, prev_advice = 0)
}

assessment_year <- params$assessment_year
advice_year <- params$advice_year
intermediate_year <- assessment_year
prev_advice_catch <- params$prev_advice

# Load the SPiCT summary object for the current assessment year.
# Generated using 1 assessment model.qmd.
# PLACEHOLDER: file will not exist until 1 assessment model.qmd has been run
# with beaked redfish data.
spict_summary <- readRDS(paste0(
  "data/model_output/spict_summaries/sum_{{STOCK_NAME_LOWER_SNAKE}}_spict_",
  assessment_year,
  ".rds"
))

state_df <- as.data.frame(spict_summary$state)
state_df$Quantity <- rownames(state_df)

f_row <- grepl("/Fmsy$", state_df$Quantity)
b_row <- grepl("/Bmsy$", state_df$Quantity)

sq_yr_decimal <- regmatches(
  state_df$Quantity[f_row],
  regexpr("\\d+\\.\\d+", state_df$Quantity[f_row])
)

dec_re <- regexpr("\\d+\\.\\d+", state_df$Quantity)
regmatches(
  state_df$Quantity,
  dec_re
) <- as.character(ceiling(as.numeric(regmatches(state_df$Quantity, dec_re))))

status_quo_F <- state_df$estimate[f_row]
status_quo_B <- state_df$estimate[b_row]
status_quo_F_lo <- state_df$cilow[f_row]
status_quo_F_hi <- state_df$ciupp[f_row]
status_quo_B_lo <- state_df$cilow[b_row]
status_quo_B_hi <- state_df$ciupp[b_row]

sq_yr_label <- sub(".*_(\\d+).*", "\\1", state_df$Quantity[f_row])

f_status <- if (status_quo_F > 1) {
  "above F~MSY~"
} else {
  "below F~MSY~"
}

b_status <- if (status_quo_B < 0.3) {
  "below B~lim~"
} else if (status_quo_B < 0.5) {
  "below MSY B~trigger~ but above B~lim~"
} else {
  "above MSY B~trigger~"
}

advice_row <- spict_summary$manTable |>
  dplyr::filter(stringr::str_detect(Scenario, "ICES advice rule"))

advised_catch <- round(advice_row$C, 0)

sq_row <- spict_summary$manTable |>
  dplyr::filter(stringr::str_detect(Scenario, "Keep current F"))

sq_catch_intermediate <- spict_summary$summary |>
  dplyr::filter(year == intermediate_year) |>
  dplyr::pull(Catch_pred.est) |>
  round(0)

last_data_year <- spict_summary$summary |>
  dplyr::filter(!is.na(total_catch)) |>
  dplyr::pull(year) |>
  max() |>
  floor()

# PLACEHOLDER: BeakedRedfish_landings_for_SPiCT.csv currently holds golden
# redfish data. Replace with beaked redfish landings before a real assessment.
annual_catches <- read.csv(
  "data/catches/{{STOCK_NAME}}_landings_for_SPiCT.csv",
  sep = ";"
) |>
  as_tibble() |>
  rename(Other = "OtherNations")

first_data_year <- min(annual_catches$Year)

# The xlsx contains both species. "s mentella" tab = beaked redfish catches.
intl_catches_df <- readxl::read_xlsx(
  "data/catches/Sebastes men and nor international catch from AFWG.xlsx",
  sheet = "s mentella"
) |>
  dplyr::filter(!is.na(Total), Year >= 1989) |>
  dplyr::mutate(Year = as.integer(Year))

max_intl_yr <- max(intl_catches_df$Year)

publication_line <- "Published X X X"

# TODO: Update these links to JRN-AFWG beaked redfish resources.
advice_doi <- "https://doi.org/PLACEHOLDER"
download_url <- "https://standardgraphs.ices.dk/stockList.aspx"
```

::: {.callout-warning}
## Exploratory assessment — not official advice

This document is an **exploratory** SPiCT surplus-production model assessment
of beaked redfish (*Sebastes mentella*) in ICES subareas 1 and 2. It is
**not official JRN-AFWG advice** and should not be used as such. The
official Joint Russian-Norwegian Working Group on Arctic Fisheries
(JRN-AFWG) assessment uses the gadget3 age-structured model
(<https://gadget-framework.github.io/>). Results here are supplementary
and exploratory only.

All catch data, survey indices, and prior values are currently
**placeholders** (golden redfish data). The advice sheet template is also
a placeholder (ICES golden redfish format) — replace with the JRN-AFWG
Word template when available.
:::

# Advice on fishing opportunities

ICES advises that when the MSY approach is applied, catches in `r advice_year` should be no more than `r format(advised_catch, big.mark = " ", scientific = FALSE)` tonnes.

*[PLACEHOLDER — the advice framework above reflects the ICES MSY approach. Adapt to JRN-AFWG advice conventions when the official framework is confirmed.]*

# Non-fisheries conservation considerations

Conservation aspects and associated management measures may exist at a national or regional level but were not reviewed here.

# Stock development over time

Fishing pressure on the stock is estimated to be `r f_status`, and the exploitable stock size is `r b_status` (Figure 1).

```{r}
#| label: fig-advicesummary
#| fig-cap: "Beaked redfish (*Sebastes mentella*) in Subareas 1 and 2. Summary of the stock assessment. Top: total catches (thousand tonnes). Bottom left: relative fishing pressure (F/F~MSY~) with 95% confidence intervals (shaded). Bottom right: relative exploitable biomass (B/B~MSY~) with 95% confidence intervals (shaded). [PLACEHOLDER — golden redfish data]"
summary_plot(x = spict_summary, lang = "eng")
```

# Catch scenarios

```{r}
#| label: tbl-catchbasis
#| tbl-cap: !expr 'paste0("Beaked redfish in Subareas 1 and 2. The basis for the catch scenarios in ", advice_year, ". The figures are rounded; calculations were done with unrounded inputs.")'
basis_tb <- tibble::tibble(
  Variable = c(
    paste0("F", sq_yr_label, "/FMSY"),
    paste0("B", advice_year, "/BMSY"),
    paste0("Predicted catch ", intermediate_year, " (tonnes)")
  ),
  Value = c(
    sprintf("%.2f", status_quo_F),
    sprintf("%.2f", sq_row$`B/Bmsy`[1]),
    format(sq_catch_intermediate, big.mark = " ", scientific = FALSE)
  ),
  Notes = c(
    paste0(
      "Fsq = Status quo fishing mortality (F",
      sq_yr_decimal,
      "/Fmsy) applied in ",
      intermediate_year,
      "."
    ),
    paste0(
      "Short-term forecast (SPiCT) after fishing at Fsq in ",
      intermediate_year,
      "."
    ),
    paste0(
      "SPiCT projection for ",
      intermediate_year,
      " at status quo F; in tonnes."
    )
  )
)

ft_basis <- flextable(basis_tb) |>
  flextable::compose(
    j = "Variable",
    i = 1,
    value = as_paragraph("F", as_sub(sq_yr_label), "/F", as_sub("MSY"))
  ) |>
  flextable::compose(
    j = "Variable",
    i = 2,
    value = as_paragraph(
      "B",
      as_sub(as.character(advice_year)),
      "/B",
      as_sub("MSY")
    )
  ) |>
  flextable::compose(
    j = "Notes",
    i = 1,
    value = as_paragraph(
      "F",
      as_sub("sq"),
      " = Status quo F (F",
      as_sub(sq_yr_decimal),
      "/F",
      as_sub("MSY"),
      ") applied in ",
      as.character(intermediate_year),
      "."
    )
  ) |>
  flextable::compose(
    j = "Notes",
    i = 2,
    value = as_paragraph(
      "Short-term forecast (SPiCT) after fishing at F",
      as_sub("sq"),
      " in ",
      as.character(intermediate_year),
      "."
    )
  ) |>
  ices_ft() |>
  align(j = c("Variable", "Value"), align = "center", part = "all") |>
  align(j = "Notes", align = "left", part = "all") |>
  width(j = "Variable", width = 1.4) |>
  width(j = "Value", width = 0.7) |>
  width(j = "Notes", width = 4.6) |>
  fit_ft_page()

ft_basis
```

\newpage

```{r}
#| label: tbl-catchscenarios
#| tbl-cap: !expr 'paste0("Beaked redfish (*Sebastes mentella*) in Subareas 1 and 2. Annual catch scenarios for ", advice_year, ". Catches are in tonnes.")'
catch_col <- paste0("Total catch\n(", advice_year, ")")
f_col <- paste0("Fishing\nmortality\nF", advice_year, "/FMSY")
b_col <- paste0("Stock size\nB", advice_year + 1, "/BMSY")
pct_bio_col <- "% biomass\nchange*"
pct_adv_col <- "% advice\nchange**"

b_current_fmt <- icesAdvice::icesRound(status_quo_B)
fn_bio <- paste0(
  "* Biomass ",
  advice_year + 1,
  " relative to biomass",
  advice_year,
  " (B",
  advice_year,
  "/BMSY = ",
  b_current_fmt,
  ")."
)
fn_adv <- if (prev_advice_catch > 0) {
  paste0(
    "** Advice for ",
    intermediate_year,
    " was ",
    format(prev_advice_catch, big.mark = " ", scientific = FALSE),
    " tonnes."
  )
} else {
  paste0(
    "** Advice for ",
    intermediate_year,
    " was 0 tonnes, and percent change cannot be calculated."
  )
}

scenarios <- spict_summary$manTable |>
  dplyr::select(Scenario, C, `B/Bmsy`, `F/Fmsy`) |>
  dplyr::mutate(
    pct_biomass_change = round((`B/Bmsy` / status_quo_B - 1) * 100, 0),
    pct_advice_change = if (prev_advice_catch > 0) {
      round((C / prev_advice_catch - 1) * 100, 0)
    } else {
      NA_real_
    },
    C = round(C, 0),
    `B/Bmsy` = icesAdvice::icesRound(`B/Bmsy`),
    `F/Fmsy` = icesAdvice::icesRound(`F/Fmsy`),
    Basis = dplyr::case_when(
      stringr::str_detect(Scenario, "ICES advice rule") ~ "Maximum sustainable yield (MSY) approach",
      stringr::str_detect(Scenario, "Fish at Fmsy") ~ "F = FMSY",
      stringr::str_detect(Scenario, "Keep current F") ~ "F = Fsq",
      stringr::str_detect(Scenario, "No fishing") ~ "F = 0",
      TRUE ~ Scenario
    ),
    Basis = factor(
      Basis,
      levels = c(
        "Maximum sustainable yield (MSY) approach",
        "F = FMSY",
        "F = Fsq",
        "F = 0"
      )
    )
  ) |>
  dplyr::arrange(Basis) |>
  dplyr::select(
    Basis, C, `F/Fmsy`, `B/Bmsy`, pct_biomass_change, pct_advice_change
  ) |>
  dplyr::rename(
    !!catch_col := C,
    !!f_col := `F/Fmsy`,
    !!b_col := `B/Bmsy`,
    !!pct_bio_col := pct_biomass_change,
    !!pct_adv_col := pct_advice_change
  )

n_cols <- ncol(scenarios)
make_group_row <- function(label) {
  row <- as.list(rep(NA, n_cols))
  names(row) <- names(scenarios)
  row[["Basis"]] <- label
  as_tibble(row)
}

scenarios_tbl <- dplyr::bind_rows(
  make_group_row("Advice basis"),
  scenarios[1, ],
  make_group_row("Other scenarios"),
  scenarios[2:nrow(scenarios), ]
) |>
  dplyr::mutate(dplyr::across(where(is.numeric), as.character))

grp_rows <- which(
  scenarios_tbl$Basis %in% c("Advice basis", "Other scenarios")
)
msy_row <- which(scenarios_tbl$Basis == levels(scenarios$Basis)[1])
fmsy_row <- which(scenarios_tbl$Basis == "F = FMSY")
fsq_row <- which(scenarios_tbl$Basis == "F = Fsq")
f0_row <- which(scenarios_tbl$Basis == "F = 0")

ft_sc <- flextable(scenarios_tbl) |>
  flextable::compose(
    part = "header", j = catch_col,
    value = as_paragraph("Total catch\n(", as.character(advice_year), ")")
  ) |>
  flextable::compose(
    part = "header", j = f_col,
    value = as_paragraph("Fishing\nmortality\nF", as_sub(as.character(advice_year)), "/F", as_sub("MSY"))
  ) |>
  flextable::compose(
    part = "header", j = b_col,
    value = as_paragraph("Stock size\nB", as_sub(as.character(advice_year + 1)), "/B", as_sub("MSY"))
  ) |>
  flextable::compose(part = "header", j = pct_bio_col, value = as_paragraph("% biomass\nchange*")) |>
  flextable::compose(part = "header", j = pct_adv_col, value = as_paragraph("% advice\nchange**")) |>
  flextable::compose(part = "body", j = "Basis", i = msy_row,
    value = as_paragraph("Maximum sustainable yield (MSY) approach")) |>
  flextable::compose(part = "body", j = "Basis", i = fmsy_row,
    value = as_paragraph("F = F", as_sub("MSY"))) |>
  flextable::compose(part = "body", j = "Basis", i = fsq_row,
    value = as_paragraph("F = F", as_sub("sq"))) |>
  flextable::compose(part = "body", j = "Basis", i = f0_row,
    value = as_paragraph("F = 0")) |>
  flextable::merge_h(i = grp_rows, part = "body") |>
  flextable::bold(i = grp_rows, part = "body") |>
  flextable::bg(i = grp_rows, bg = "#F5F5F5", part = "body") |>
  flextable::align(i = grp_rows, align = "left", part = "body") |>
  flextable::colformat_char(j = pct_adv_col, na_str = "–") |>
  ices_ft() |>
  flextable::align(j = 2:n_cols, align = "center", part = "all") |>
  flextable::align(j = "Basis", align = "left", part = "all") |>
  flextable::width(j = "Basis", width = 3.0) |>
  flextable::width(j = catch_col, width = 0.65) |>
  flextable::width(j = f_col, width = 0.85) |>
  flextable::width(j = b_col, width = 0.85) |>
  flextable::width(j = pct_bio_col, width = 0.65) |>
  flextable::width(j = pct_adv_col, width = 0.65) |>
  fit_ft_page() |>
  flextable::add_footer_lines(fn_bio) |>
  flextable::add_footer_lines(fn_adv) |>
  flextable::compose(
    part = "footer", i = 1, j = 1,
    value = as_paragraph(
      "* Biomass ", as.character(advice_year + 1),
      " relative to biomass ", as.character(advice_year),
      " (B", as_sub(as.character(advice_year)), "/B", as_sub("MSY"), " = ", b_current_fmt, ")."
    )
  ) |>
  flextable::fontsize(size = 8, part = "footer") |>
  flextable::align(align = "left", part = "footer")

ft_sc
```

# Basis of the advice

```{r}
#| label: tbl-advicebasis
#| tbl-cap: "Beaked redfish in Subareas 1 and 2. The basis for the advice."
advice_basis <- tibble::tibble(
  Item = c("Advice basis", "Management plan"),
  Description = c(
    "MSY approach (ICES MSY hockey-stick advice rule with Blim and the 35th percentile of the catch distribution). [PLACEHOLDER — adapt to JRN-AFWG advice framework]",
    "ICES is not aware of any agreed precautionary management plan for the stock. ICES MSY approach applied. [PLACEHOLDER — confirm JRN-AFWG management plan status]"
  )
)

ft_basis2 <- flextable(advice_basis) |>
  delete_part(part = "header") |>
  flextable::compose(
    j = "Description", i = 1,
    value = as_paragraph(
      "MSY approach (ICES MSY hockey-stick advice rule with B", as_sub("lim"),
      " and 35th percentile of the catch distribution). [PLACEHOLDER]"
    )
  ) |>
  bg(j = "Item", bg = "#E8EAEA", part = "body") |>
  border_inner(fp_border(color = "black", width = 0.5)) |>
  border_outer(fp_border(color = "black", width = 0.75)) |>
  font(fontname = "Calibri", part = "all") |>
  fontsize(size = 9, part = "all") |>
  align(j = "Item", align = "left", part = "body") |>
  align(j = "Description", align = "left", part = "body") |>
  bold(j = "Item", part = "body") |>
  width(j = "Item", width = 1.5) |>
  width(j = "Description", width = 5.0) |>
  fit_ft_page()

ft_basis2
```

# Quality of the assessment

**[PLACEHOLDER — rewrite this section once beaked redfish data and a confirmed model configuration are in place.]**

This is an exploratory SPiCT surplus production model [@pedersen2017] fitted to total annual catches (`r first_data_year`–`r last_data_year`) and a biomass bottom-trawl survey index (`r spict_summary$summary |> dplyr::filter(!is.na(index)) |> dplyr::pull(year) |> floor() |> range() |> paste(collapse = "-")`). The model uses a fixed Schaefer shape, placeholder priors on initial biomass depletion and the intrinsic growth rate, and a catch standard-deviation multiplier reflecting estimated data quality. All data and priors are currently golden redfish placeholders.

The official JRN-AFWG beaked redfish assessment is conducted with the gadget3 age-structured model (<https://gadget-framework.github.io/>).

# Issues relevant for the advice

**[PLACEHOLDER — replace with beaked redfish–specific stock issues.]**

The exploratory advice is based on the ICES MSY framework using the 35th percentile of the projected catch distribution [@ices2020a]. Beaked redfish (*Sebastes mentella*) in ICES Subareas 1 and 2 is a long-lived, slow-growing species. Key issues expected to be relevant include:

- Mixing of *S. mentella* and *S. norvegicus* in historical catch and survey records.
- Population structure within ICES Subareas 1–2.
- Uncertainty in historical catches.
- Survey availability and representativeness.

These should be reviewed against the most recent JRN-AFWG assessment report before updating this section.

<!-- \newpage -->

# Reference points

```{r}
#| label: tbl-refpoints
#| tbl-cap: "Beaked redfish in Subareas 1 and 2. Reference points, values, and their technical basis. No absolute reference points are defined; the SPiCT model provides reference points on the relative scale only."
ref_tb <- tibble::tibble(
  Framework = c("MSY approach", "MSY approach", "Precautionary approach"),
  `Reference point` = c("MSY Btrigger", "FMSY", "Blim"),
  Value = c("B/BMSY = 0.5", "F/FMSY = 1", "B/BMSY = 0.3"),
  `Technical basis` = c(
    "Relative value from the SPiCT model. BMSY is estimated directly from the SPiCT assessment and changes when the assessment is updated.",
    "Relative value from the SPiCT model. FMSY is estimated directly from the SPiCT assessment and changes when the assessment is updated.",
    "Set at B/BMSY = 0.3 following ICES standard for SPiCT stocks (ICES, 2021)."
  )
)

ft_ref <- flextable(ref_tb) |>
  flextable::compose(i = 1, j = "Reference point", value = as_paragraph("MSY B", as_sub("trigger"))) |>
  flextable::compose(i = 2, j = "Reference point", value = as_paragraph("F", as_sub("MSY"))) |>
  flextable::compose(i = 3, j = "Reference point", value = as_paragraph("B", as_sub("lim"))) |>
  flextable::compose(i = 1, j = "Value", value = as_paragraph("B/B", as_sub("MSY"), " = 0.5")) |>
  flextable::compose(i = 2, j = "Value", value = as_paragraph("F/F", as_sub("MSY"), " = 1")) |>
  flextable::compose(i = 3, j = "Value", value = as_paragraph("B/B", as_sub("MSY"), " = 0.3")) |>
  flextable::compose(
    i = 1, j = "Technical basis",
    value = as_paragraph(
      "Relative reference points from the SPiCT model. B", as_sub("MSY"),
      " is estimated directly from the SPiCT assessment and changes when the assessment is updated."
    )
  ) |>
  flextable::compose(
    i = 2, j = "Technical basis",
    value = as_paragraph(
      "Relative reference points from the SPiCT model. F", as_sub("MSY"),
      " is estimated directly from the SPiCT assessment and changes when the assessment is updated."
    )
  ) |>
  flextable::compose(
    i = 3, j = "Technical basis",
    value = as_paragraph("Set at B/B", as_sub("MSY"), " = 0.3 following ICES standard for SPiCT stocks (ICES, 2021).")
  ) |>
  merge_at(i = 1:2, j = "Framework") |>
  ices_ft() |>
  align(j = c("Framework", "Reference point", "Value"), align = "center", part = "all") |>
  align(j = "Technical basis", align = "left", part = "all") |>
  width(j = "Framework", width = 1.15) |>
  width(j = "Reference point", width = 1.15) |>
  width(j = "Value", width = 1.05) |>
  width(j = "Technical basis", width = 3.15) |>
  fit_ft_page()

ft_ref
```

# Basis of the assessment

```{r}
#| label: tbl-assbasis
#| tbl-cap: "Beaked redfish in Subareas 1 and 2. Basis of the assessment and advice."
ass_basis <- tibble::tibble(
  Item = c(
    "Stock data category",
    "Assessment type",
    "Input data",
    "Discards",
    "Other information",
    "Working group"
  ),
  Description = c(
    "PLACEHOLDER — confirm ICES stock data category for reb.27.1-2.",
    "SPiCT surplus production model (Pedersen and Berg, 2017). Exploratory; official assessment uses gadget3.",
    paste0(
      "PLACEHOLDER — annual total landings from Norway, Russia, and other countries (",
      first_data_year, "–", last_data_year,
      "; data are golden redfish placeholders). ",
      "Compiled spatiotemporal biomass survey index (PLACEHOLDER — golden redfish index). ",
      "Scaled to its mean."
    ),
    "Discards are not included in the assessment; assumed negligible. [PLACEHOLDER — verify for beaked redfish]",
    "PLACEHOLDER — describe benchmark / review history for beaked redfish SPiCT exploration.",
    "Joint Russian-Norwegian Working Group on Arctic Fisheries (JRN-AFWG)."
  )
)

ft_ass <- flextable(ass_basis) |>
  delete_part(part = "header") |>
  bg(j = "Item", bg = "#E8EAEA", part = "body") |>
  border_inner(fp_border(color = "black", width = 0.5)) |>
  border_outer(fp_border(color = "black", width = 0.75)) |>
  font(fontname = "Calibri", part = "all") |>
  fontsize(size = 9, part = "all") |>
  align(j = "Item", align = "left", part = "body") |>
  align(j = "Description", align = "left", part = "body") |>
  bold(j = "Item", part = "body") |>
  width(j = "Item", width = 1.84) |>
  width(j = "Description", width = 4.66) |>
  fit_ft_page()

ft_ass
```

# History of the advice, catch, and management

```{r}
#| label: tbl-catchmanagement
#| tbl-cap: !expr 'paste0("Beaked redfish in Subareas 1 and 2. History of catch and management. Catches in tonnes. [PLACEHOLDER — replace advice history with JRN-AFWG beaked redfish records]")'

# PLACEHOLDER: This table covers only recent years as a structural placeholder.
# Replace the ICES Advice strings with the actual JRN-AFWG beaked redfish advice
# history, extending the Year range to match.
# The annual-update task: extend `ICES Advice` when assessment_year advances.

advice_start_year <- 2015  # PLACEHOLDER: set to first year with formal JRN-AFWG advice

advice_mgmt <- tibble::tibble(
  Year = c(advice_start_year:assessment_year, advice_year),
  `ICES Advice` = c(
    rep(
      "PLACEHOLDER – replace with JRN-AFWG beaked redfish advice",
      assessment_year - advice_start_year + 1
    ),
    "MSY approach (exploratory SPiCT)"  # advice_year
  ),
  `Catch corresponding\nto advice` = c(
    rep(NA_real_, assessment_year - advice_start_year + 1),
    advised_catch
  ),
  `Agreed TAC` = rep(NA_real_, advice_year - advice_start_year + 1)
)

est_catches <- spict_summary$summary |>
  dplyr::filter(year == round(year, 0)) |>
  dplyr::transmute(
    Year = as.integer(floor(year)),
    `Catches` = round(total_catch, 0)
  )

advice_mgmt <- advice_mgmt |> dplyr::left_join(est_catches, by = "Year")

last_catch_row <- which(advice_mgmt$Year == last_data_year)

ft_mgmt <- flextable(advice_mgmt) |>
  colformat_int(j = "Year", big.mark = "") |>
  colformat_double(
    j = c("Catch corresponding\nto advice", "Agreed TAC", "Catches"),
    big.mark = " ",
    digits = 0,
    na_str = "–"
  ) |>
  ices_ft() |>
  align(j = "ICES Advice", align = "left", part = "all") |>
  align(
    j = c("Year", "Catch corresponding\nto advice", "Agreed TAC", "Catches"),
    align = "center",
    part = "all"
  ) |>
  width(j = "Year", width = 0.45) |>
  width(j = "ICES Advice", width = 2.85) |>
  width(j = "Catch corresponding\nto advice", width = 1.05) |>
  width(j = "Agreed TAC", width = 0.9) |>
  width(j = "Catches", width = 1.0) |>
  fit_ft_page() |>
  flextable::compose(
    i = last_catch_row,
    j = "Catches",
    value = as_paragraph(
      format(
        advice_mgmt$Catches[last_catch_row],
        big.mark = " ",
        scientific = FALSE
      ),
      as_sup("*")
    )
  ) |>
  flextable::add_footer_lines("* Preliminary") |>
  flextable::fontsize(size = 8, part = "footer") |>
  flextable::align(align = "left", part = "footer")

ft_mgmt
```

\newpage

```{r}
#| label: tbl-gearfleet
#| tbl-cap: !expr 'paste0("Beaked redfish in Subareas 1 and 2. Catch distribution by gear in ", max_intl_yr, " as estimated. [PLACEHOLDER — golden redfish gear data]")'
gear_yr <- read.csv("data/catches/landings_by_gear_pct_allNations.csv") |>
  dplyr::rename_with(tolower) |>
  dplyr::filter(year == max_intl_yr)

total_intl <- intl_catches_df |>
  dplyr::filter(Year == max_intl_yr) |>
  dplyr::pull(Total)
total_fmt_intl <- formatC(round(total_intl, 0), format = "d", big.mark = " ")

gear_total_nor <- sum(gear_yr$tonnes)
gear_fmt_nor <- formatC(round(gear_total_nor, 0), format = "d", big.mark = " ")

gear_cats <- gear_yr |>
  dplyr::mutate(
    cat = dplyr::case_when(
      gear == "Gillnets" ~ "Gillnet",
      gear == "Longlines" ~ "Longline",
      gear == "Bottom trawls" ~ "Trawl",
      TRUE ~ "Other gears"
    )
  ) |>
  dplyr::group_by(cat) |>
  dplyr::summarise(tonnes = sum(tonnes), .groups = "drop")

pct_label <- function(gear) {
  v <- gear_cats$tonnes[gear_cats$cat == gear]
  sprintf("%.0f%% %s", v / gear_total_nor * 100, tolower(gear))
}

body_df <- data.frame(
  col1 = c(paste0(total_fmt_intl, " tonnes"), ""),
  col2 = c(pct_label("Gillnet"), paste0(gear_fmt_nor, " tonnes")),
  col3 = c(pct_label("Longline"), ""),
  col4 = c(pct_label("Trawl"), ""),
  col5 = c(pct_label("Other gears"), ""),
  col6 = c("Assumed to be negligible", ""),
  col7 = c("Unknown", ""),
  stringsAsFactors = FALSE
)

flextable(body_df) |>
  set_header_labels(
    col1 = paste0("Total commercial catch (", max_intl_yr, ")"),
    col2 = "Commercial landings",
    col3 = "Commercial landings",
    col4 = "Commercial landings",
    col5 = "Commercial landings",
    col6 = "Discards",
    col7 = "Recreational fisheries"
  ) |>
  ices_ft() |>
  merge_h(part = "header") |>
  merge_at(i = 1:2, j = 1, part = "body") |>
  merge_at(i = 1:2, j = 6, part = "body") |>
  merge_at(i = 1:2, j = 7, part = "body") |>
  merge_at(i = 2, j = 2:5, part = "body") |>
  align(align = "center", part = "all") |>
  valign(valign = "center", part = "body")
```

\newpage

```{r}
#| label: tbl-catchhistory
#| tbl-cap: !expr 'paste0("Beaked redfish (*Sebastes mentella*) in Subareas 1 and 2. History of estimated commercial catches (tonnes) by country, 1989–", max_intl_yr, ". The most recent year is preliminary. [PLACEHOLDER — verify column names against s mentella tab]")'
catch_hist <- intl_catches_df |>
  dplyr::mutate(
    uk_pre = dplyr::if_else(
      "UK (Eng. & Wales)" %in% names(intl_catches_df),
      `UK (Eng. & Wales)`,
      NA_real_
    ),
    uk_post = dplyr::if_else(Year >= 2000, UK, NA_real_)
  ) |>
  dplyr::transmute(
    Year = dplyr::if_else(
      Year == max_intl_yr,
      paste0(Year, "*"),
      as.character(Year)
    ),
    Norway,
    Russia,
    Total
  )

ft_catch <- flextable(catch_hist) |>
  colformat_char(j = "Year") |>
  colformat_double(
    j = 2:(ncol(catch_hist)),
    big.mark = " ",
    digits = 0,
    na_str = "–"
  ) |>
  ices_ft() |>
  fontsize(size = 7, part = "all") |>
  align(align = "center", part = "all") |>
  autofit() |>
  fit_ft_page() |>
  add_footer_lines("* Preliminary figures.") |>
  add_footer_lines(
    "NOTE: Column set is a placeholder. Verify against the 's mentella' tab in the xlsx for the full country breakdown."
  ) |>
  fontsize(size = 7, part = "footer") |>
  padding(padding = 1, part = "footer")

ft_catch
```

\newpage

# Summary of the assessment

```{r}
#| label: tbl-assessmentsummary
#| tbl-cap: Beaked redfish in Subareas 1 and 2. SPiCT assessment summary. Relative exploitable biomass (B/B~MSY~), total catch (tonnes), and relative fishing mortality (F/F~MSY~), with 95% confidence intervals (low and high). [PLACEHOLDER — golden redfish data]
assess_tb <- spict_summary$summary |>
  dplyr::filter(year == round(year, 0), year < advice_year) |>
  dplyr::transmute(
    Year = as.integer(floor(year)),
    `B/BMSY (low)` = round(exp(BBmsy.ll), 2),
    `B/BMSY` = round(exp(BBmsy.est), 2),
    `B/BMSY (high)` = round(exp(BBmsy.ul), 2),
    `Catch (t)` = round(total_catch, 0),
    `F/FMSY (low)` = dplyr::if_else(
      Year < assessment_year, round(exp(FFmsy.ll), 2), NA_real_
    ),
    `F/FMSY` = dplyr::if_else(
      Year < assessment_year, round(exp(FFmsy.est), 2), NA_real_
    ),
    `F/FMSY (high)` = dplyr::if_else(
      Year < assessment_year, round(exp(FFmsy.ul), 2), NA_real_
    )
  )

ft_ass_sum <- flextable(assess_tb) |>
  colformat_int(j = 1, big.mark = "") |>
  colformat_double(j = 2:4, digits = 2, big.mark = "") |>
  colformat_double(j = 5, digits = 0, big.mark = " ") |>
  colformat_double(j = 6:8, digits = 2, big.mark = "", na_str = "–") |>
  flextable::compose(j = "B/BMSY (low)", part = "header",
    value = as_paragraph("B/B", as_sub("MSY"), "\n(low)")) |>
  flextable::compose(j = "B/BMSY", part = "header",
    value = as_paragraph("B/B", as_sub("MSY"))) |>
  flextable::compose(j = "B/BMSY (high)", part = "header",
    value = as_paragraph("B/B", as_sub("MSY"), "\n(high)")) |>
  flextable::compose(j = "F/FMSY (low)", part = "header",
    value = as_paragraph("F/F", as_sub("MSY"), "\n(low)")) |>
  flextable::compose(j = "F/FMSY", part = "header",
    value = as_paragraph("F/F", as_sub("MSY"))) |>
  flextable::compose(j = "F/FMSY (high)", part = "header",
    value = as_paragraph("F/F", as_sub("MSY"), "\n(high)")) |>
  ices_ft() |>
  align(align = "center", part = "all") |>
  fit_ft_page()

ft_ass_sum
```

\newpage

# Sources and references

::: {#refs}
:::

```{r}
#| results: asis
if (!knitr::is_latex_output()) {
  # TODO: Update citation text for JRN-AFWG beaked redfish once official
  # assessment documents are available.
  citation_pre <- paste0(
    "Recommended citation: ICES. ",
    assessment_year,
    ". Beaked redfish (",
    "Sebastes mentella",
    ") in subareas 1 and 2 (Northeast Arctic). "
  )
  citation_post <- paste0(
    " Report of the ICES Advisory Committee, ",
    assessment_year,
    ". ICES Advice ",
    assessment_year,
    ", reb.27.1-2, ",
    advice_doi
  )

  cite_txt <- officer::fp_text(font.family = "Calibri", font.size = 9)
  cite_txt_italic <- officer::fp_text(
    font.family = "Calibri", font.size = 9, italic = TRUE
  )

  box_border <- officer::fp_border(color = "black", width = 0.75)

  ft_box <- flextable::flextable(tibble::tibble(content = c("link", "citation"))) |>
    flextable::delete_part(part = "header") |>
    flextable::compose(
      i = 1, j = "content",
      value = flextable::as_paragraph(flextable::hyperlink_text(
        "Download the stock assessment data and figures\n",
        url = if (nzchar(download_url)) download_url else advice_doi,
        props = officer::fp_text(
          color = "#0B58CA", underlined = TRUE,
          font.family = "Calibri", font.size = 9
        )
      ))
    ) |>
    flextable::compose(
      i = 2, j = "content",
      value = flextable::as_paragraph(
        flextable::as_chunk(citation_pre, props = cite_txt),
        flextable::as_chunk("In", props = cite_txt_italic),
        flextable::as_chunk(citation_post, props = cite_txt)
      )
    ) |>
    flextable::border_remove() |>
    flextable::border_outer(border = box_border, part = "body") |>
    flextable::padding(
      padding.top = 6, padding.bottom = 6,
      padding.left = 6, padding.right = 6, part = "body"
    ) |>
    flextable::align(align = "left", part = "body") |>
    flextable::width(j = "content", width = page_width_in)

  ft_box
}
```
