---
title: "SPiCT candidate comparison"
subtitle: "Exploration"
date: today
published-title: "Version"
format:
  html:
    embed-resources: true
    theme: cosmo
    toc: true
    toc-depth: 3
    toc-expand: true
    code-fold: true
    code-summary: "Show code"
    fig-format: jpeg
execute:
  warning: false
  message: false
params:
  description: NULL   # What question this comparison answers
  candidates: NULL    # Candidate names saved by R/explore_fit.R
  output_dir: NULL    # Where those candidates live
---

<!--
Rendered by R/explore_compare.R. Candidates fitted to DIFFERENT DATA are not comparable by
likelihood or AIC; their trajectories still are. Say which comparison you are making.
-->

```{r knit-setup}
#| include: false
#| cache: false
knitr::opts_knit$set(root.dir = here::here())

knitr::knit_hooks$set(timeit = local({
  now <- NULL
  function(before, options) {
    if (before) {
      now <<- Sys.time()
    } else {
      res <- round(difftime(Sys.time(), now, units = "mins"), 1)
      now <<- NULL
      print(paste("Time:", as.character(res), "min"))
    }
  }
}))
```

```{r params}
source(here::here("R", "0_setup.R"))
source(here::here("R", "report_helpers.R"))
source(here::here("R", "spict_helpers.R"))
source(here::here("R", "spict_exploration.R"))

description <- params$description
models <- params$candidates
model_dir <- params$output_dir

cat(description, "\n")
```



```{r collectmodels}

ms <- lapply(models, function(m) {
  cat("Loading model:", m, "\n")
  out <- readRDS(file.path(model_dir, paste0("candidate_", m, ".rds")))
  attributes(out)$model_name <- m
  return(out)
})

names(ms) <- models
```

# Models convergence

```{r convergence}
converged <- vapply(ms, function(m) isTRUE(m$opt$convergence == 0), logical(1))

for (i in seq_along(ms)) {
  cat("Candidate:", names(ms)[i], "-> convergence:", ms[[i]]$opt$convergence, "\n")
}

# A candidate that did not converge is dropped rather than plotted: nothing it reports is
# meaningful, and a non-converged trajectory beside converged ones invites comparison.
if (any(!converged)) {
  cat("\nDropped (did not converge):", paste(names(ms)[!converged], collapse = ", "), "\n")
}
ms <- ms[converged]
if (!length(ms)) stop("No candidate converged; there is nothing to compare.")

ms_n <- names(ms)
model_names <- ms_n
gg_cols <- scales::hue_pal()(length(ms_n))

# good_ms <- list()

# for (mn in ms_n) {
#   fit <- ms[[mn]]
#   conv <- as.character(fit$opt$convergence)

#   if (conv == "0") {
#     good_ms[[mn]] <- fit
#   }

#   cat(mn, "-> convergence:", conv, "\n")
# }

# ms <- good_ms
# ms_n <- names(ms)

```


# Plotspict compare

```{r plotspictgeneral}
tryCatch(
  {
    plotspict.compare(ms, col = gg_cols)
    plotspict.compare(ms, CI = 0, col = gg_cols)
  },
  error = function(e) {
    message("\n An error occurred:\n", e$message)
  }
)
```

## Biomass

```{r biomass}
tryCatch(
  {
    plotspict.compare(ms, varname = "B", plot.legend = 2, col = gg_cols)
    plotspict.compare(ms, varname = "B", CI = 0, col = gg_cols)
    plotspict.compare(ms, varname = "BBmsy", plot.legend = 2, col = gg_cols)
    plotspict.compare(ms, varname = "BBmsy", CI = 0, col = gg_cols)
  },
  error = function(e) {
    message("\n An error occurred:\n", e$message)
  }
)
```

## Fishing mortality

```{r fmortality}
tryCatch(
  {
    plotspict.compare(ms, varname = "F", col = gg_cols)
    plotspict.compare(ms, varname = "F", CI = 0, col = gg_cols)
    plotspict.compare(ms, varname = "FFmsy", col = gg_cols)
    plotspict.compare(ms, varname = "FFmsy", CI = 0, col = gg_cols)
  },
  error = function(e) {
    message("\n An error occurred:\n", e$message)
  }
)
```

## Catch and Production

```{r catchandprod}
tryCatch(
  {
    plotspict.compare(ms, varname = "C", col = gg_cols)
    plotspict.compare(ms, varname = "C", CI = 0, col = gg_cols)
    plotspict.compare(ms, varname = "P", col = gg_cols)
    plotspict.compare(ms, varname = "P", CI = 0, col = gg_cols)
  },
  error = function(e) {
    message("\n An error occurred:\n", e$message)
  }
)
```

# Reference points

## MSY

```{r msy}
rp_vars <- c("logMSY")

comp_plot(ms = ms, variables = rp_vars)

```

## Bmsy

```{r bmsy}
rp_vars <- c('logBmsy')

comp_plot(ms = ms, variables = rp_vars)
```

## Fmsy

```{r fmsy}
rp_vars <- c('logFmsy')

comp_plot(ms = ms, variables = rp_vars)

```

# State of the stock

## Final year biomass

```{r bbmsy}
rp_vars <- c("logBlBmsy")

comp_plot(ms = ms, variables = rp_vars)
```

```{r bl}
rp_vars <- c("logBl")

comp_plot(ms = ms, variables = rp_vars)
```

## Final year fishing mortality

```{r ffmsy}
rp_vars <- c("logFlFmsy")
comp_plot(ms = ms, variables = rp_vars)
```

```{r fl}
rp_vars <- c("logFl")
comp_plot(ms = ms, variables = rp_vars)
```

# Important parameters

## BKfrac

```{r bkfrac}
rp_vars <- c("logbkfrac")
comp_plot(ms = ms, variables = rp_vars)
```

## n

```{r logn}
rp_vars <- c("logn")
comp_plot(ms = ms, variables = rp_vars)
```

## r

```{r logr}
rp_vars <- c("logr")
comp_plot(ms = ms, variables = rp_vars)
```

## K

```{r logK}
rp_vars <- c("logK")
comp_plot(ms = ms, variables = rp_vars)
```

# Standard deviation values

## sdc

```{r sdc}
sd_values <- c("logsdc")
comp_plot(ms = ms, variables = sd_values)
```

## sdi

```{r sdi}
sd_values <- c("logsdi")
comp_plot(ms = ms, variables = sd_values)
```

## sdb

```{r sdb}
sd_values <- c("logsdb")
comp_plot(ms = ms, variables = sd_values)
```

## sdf

```{r sdf}
sd_values <- c("logsdf")
comp_plot(ms = ms, variables = sd_values)

```

## alpha

```{r alpha}
sd_values <- c("logalpha")
comp_plot(ms = ms, variables = sd_values)
```

## beta

```{r beta}
sd_values <- c("logbeta")
comp_plot(ms = ms, variables = sd_values)
```

# Catch observed vs fitted

Observed catches are extracted from the first model in the list.

```{r obscatch}
comp_plot2(ms = ms, variables = c("logCpred"))
```

# Index observed vs fitted

Observed index is extracted from the first model in the list.

```{r obsindex}
comp_plot2(ms = ms, variables = c("logIpred"))
```


