---
title: "SPiCT candidate fit"
subtitle: "Exploration"
date: today
published-title: "Version"
format:
  html:
    embed-resources: true
    theme: cosmo
    toc: true
    toc-depth: 3
    toc-expand: true
    code-fold: true
    code-summary: "Show code"
    fig-format: jpeg
execute:
  warning: false
  message: false
params:
  run_name: NULL          # Short unique name for this candidate
  run_description: NULL   # One sentence: what this candidate changes and why
  fit_path: NULL          # Path to the fit saved by R/explore_fit.R
  run_ini_trials: 10
  run_retro: false
  retro_years: 5
  hindcast_years: 5
  run_manage: true
---

<!--
Rendered by R/explore_fit.R, once per candidate configuration. The fit is made there and saved;
this document reports it. Diagnostics and their acceptance criteria are in the pack's
knowledge/diagnostics.md.
-->

```{r knit-setup}
#| include: false
#| cache: false
knitr::opts_knit$set(root.dir = here::here())

knitr::knit_hooks$set(timeit = local({
  now <- NULL
  function(before, options) {
    if (before) {
      now <<- Sys.time()
    } else {
      res <- round(difftime(Sys.time(), now, units = "mins"), 1)
      now <<- NULL
      print(paste("Time:", as.character(res), "min"))
    }
  }
}))
```

```{r params}
source(here::here("R", "0_setup.R"))
source(here::here("R", "report_helpers.R"))
source(here::here("R", "spict_helpers.R"))
source(here::here("R", "spict_exploration.R"))
source(here::here("R", "advice_tables.R"))
source(here::here("R", "ices_plots.R"))

model <- params$run_name
description <- params$run_description

ini_trials <- params$run_ini_trials
nretroyears <- params$retro_years
nhindcastyears <- params$hindcast_years

cat("Candidate:", model, "\n")
cat("Description:", description, "\n")
```

<details>
<summary>Unfold to see R package versions and system information used to generate this document</summary>
```{r}
#| label: sys-info
sessionInfo()
```
</details>

```{r loadfit}
# The fit was made and saved by R/explore_fit.R. This document reports it rather than
# refitting, so the report and the saved candidate cannot disagree.
res <- readRDS(params$fit_path)
inp <- res$inp

if (!identical(res$opt$convergence, 0) && !identical(res$opt$convergence, 0L)) {
  cat("**The candidate did not converge** (optimiser exit code ", res$opt$convergence,
      "). Nothing below it is meaningful.\n", sep = "")
  knitr::knit_exit()
}
```

# Summary and  parameter correlation matrix

```{r summary}
#| echo: true
summary(res)
all(is.finite(res$sd))
cov2cor(res$cov.fixed)
```

# Magnitude of uncertainty and initial values sensitivity

```{r initialvalues}
#| echo: true
calc.om(res)
check.ini(inp, ntrials = ini_trials)
```

# General plots

```{r generalplots}
plot(res)
```

## Biomass

```{r biomass}
tryCatch(
  {
    plotspict.bbmsy(res)
  },
  error = function(e) {
    message("Plot skipped: ", e$message)
  }
)

tryCatch(
  {
    plotspict.biomass(res)
  },
  error = function(e) {
    message("Plot skipped: ", e$message)
  }
)
```

## Catch and F

```{r catch}
tryCatch(
  {
    plotspict.catch(res)
  },
  error = function(e) {
    message("Plot skipped: ", e$message)
  }
)

tryCatch(
  {
    plotspict.f(res)
  },
  error = function(e) {
    message("Plot skipped: ", e$message)
  }
)

tryCatch(
  {
    plotspict.ffmsy(res)
  },
  error = function(e) {
    message("Plot skipped: ", e$message)
  }
)
```

## Kobe and Years to Bmsy

```{r kobe}
tryCatch(
  {
    plotspict.fb(res)
  },
  error = function(e) {
    message("Plot skipped: ", e$message)
  }
)

tryCatch(
  {
    plotspict.tc(res)
  },
  error = function(e) {
    message("Plot skipped: ", e$message)
  }
)


```

## Production curve and priors

```{r priors}
tryCatch(
  {
    plotspict.production(res)
  },
  error = function(e) {
    message("Plot skipped: ", e$message)
  }
)


tryCatch(
  {
    plotspict.priors(res)
  },
  error = function(e) {
    message("Plot skipped: ", e$message)
  }
)
```

# Catch observed vs fitted

```{r obscatch}

tryCatch(
  {
    comp_plot2(ms = c("res"), variables = c("logCpred"))
  },
  error = function(e) {
    message("Plot skipped: ", e$message)
  }
)

```

# Index observed vs fitted

```{r obsindex}

tryCatch(
  {
    comp_plot2(ms = c("res"), variables = c("logIpred"))
  },
  error = function(e) {
    message("Plot skipped: ", e$message)
  }
)
```

# OSA residuals

```{r osa, fig.height = 10}

tryCatch(
  {
    res <- calc.osa.resid(res)
    plotspict.diagnostic(res)
  },
  error = function(e) {
    message("Plot skipped: ", e$message)
  }
)

```

# Process residuals

```{r process, fig.height = 10}

tryCatch(
  {
    res <- calc.process.resid(res)
    plotspict.diagnostic.process(res)
  },
  error = function(e) {
    message("Plot skipped: ", e$message)
  }
)

```

# Retros and hindcasting

```{r retros, eval=params$run_retro}

tryCatch(
  {
    res <- retro(res, nretroyear = nretroyears, mc.cores = 1)
    plotspict.retro(res)
    plotspict.retro.fixed(res)
  },
  error = function(e) {
    message("Plot skipped: ", e$message)
  }
)

tryCatch(
  {
    res <- hindcast(res, npeels = nhindcastyears)
    plotspict.hindcast(res)
  },
  error = function(e) {
    message("Plot skipped: ", e$message)
  }
)


```

# Management scenarios

```{r manage, eval=params$run_manage}

tryCatch(
  {
    TACyear <- res$inp$timeC[length(res$inp$timeC)] + 2

    man <- manage(
      res,
      scenarios = c("currentF", "Fmsy", "noF", "ices"),
      maninterval = c(TACyear, TACyear + 1),
      maneval = TACyear + 1
    )

    # man <- add.man.scenario(
    #   man,
    #   scenarioTitle = "15th percentile",
    #   maninterval = c(TACyear, TACyear + 1),
    #   maneval = TACyear + 1,
    #   fractiles = list(catch = 0.15),
    #   breakpointB = 0.5,
    #   safeguardB = list(limitB = 0.3, prob = 0.95)
    # )

    manOutput <- sumspict.manage(man, include.unc = TRUE)

    risk <- spictRisk(man, bmsyfrac = 0.5, years = c(TACyear - 1, TACyear)) # 0.5 = Btrigger

    plotspict.hcr(man)

    manTable <- bind_cols(
      manOutput$est,
      manOutput$unc,
      risk %>%
        mutate(across(BbelowBmsy:FaboveFlim, ~ . * 100)) %>% # change to percent?
        pivot_wider(
          id_cols = Scenario,
          values_from = BbelowBmsy:FaboveFlim,
          names_from = Year
        )
    ) %>%
      mutate(Scenario = rownames(manOutput$est)) %>%
      relocate(Scenario)
  },
  error = function(e) {
    message("\n An error occurred in the management chunk:\n", e$message)
  }
)
```

# SPiCT summary

```{r spict-summary}
# The same summary object the production assessment saves, built by the shared helper rather
# than by a second implementation here — an exploration report that summarises a fit
# differently from the assessment is comparing two things, not one.
tryCatch(
  {
    spict_summary <- spict_summary_object(
      man,
      assessment_year = TACyear - 1,
      man_table = manTable,
      checks = tryCatch(acceptance_checks(res), error = function(e) NULL)
    )
    spict_summary$risk <- risk

    dest <- file.path(output_dir, paste0("candidate_summary_", model, ".rds"))
    saveRDS(spict_summary, file = dest, compress = "xz")
  },
  error = function(e) {
    message("\n An error occurred in the SPiCT summary chunk:\n", e$message)
  }
)
```

```{r}
#| label: fig-summary-plot
#| fig-cap: "ICES assessment summary plot."
tryCatch(
  {
    summary_plot(spict_summary)
  },
  error = function(e) {
    message("\n An error occurred in the ICES summary plot chunk:\n", e$message)
  }
)
```






