---
format: 
  html:
    embed-resources: true
    theme: cosmo
    toc: true
    toc-depth: 3
    toc-expand: true
execute:
  echo: false
  warning: false
  message: false
params:
  description: NULL
  models: NULL
  model_directory: NULL
---

```{r knit-setup, eval = TRUE, include = FALSE, cache = FALSE}

knitr::opts_knit$set(root.dir = '../../')

knitr::knit_hooks$set(
  timeit = local({
    now = NULL
    function(before, options) {
      if (before) {
        now <<- Sys.time()
      } else {
        res = round(difftime(Sys.time(), now, units = "mins"), 1)
        now <<- NULL
        # use options$label if you want the chunk label as well
        print(paste('Time:', as.character(res), "min"))
      }
    }
  })
)
```


```{r params}
# Access parameters
description <- params$description
models <- params$models
model_dir <- params$model_directory

cat(description, "\n")
```

```{r additionalfuncs}
# Additional spict functions
source("src/exploration/additional_spict_funcs.R")
```


```{r collectmodels}

ms <- lapply(models, function(m) {
  cat("Loading model:", m, "\n")
  out <- readRDS(file.path(model_dir, paste0("res_", m, ".rds")))
  attributes(out)$model_name <- m
  return(out)
})

names(ms) <- models

# for (m in models) {
#   assign(
#     x = paste0("res_", m),
#     value = get(load(paste0("_saved_models/", "res_", m, ".rda")))
#   )
# }

# ms_n <- map(models, ~ paste0("res_", .x))

# ms <- setNames(lapply(ms_n, get), ms_n)

```

# Models convergence

```{r convergence}
good_ms <- sapply(seq_along(ms), function(i) {
  m <- ms[[i]]
  conv <- as.character(m$opt$convergence)
  cat("Model:", names(ms)[i], "-> convergence:", conv, "\n")

  if (conv == "0") {
    return(names(ms)[i])
  }
})

ms <- ms[good_ms]
ms_n <- names(ms)
model_names <- sub("res_", "", ms_n)
gg_cols <- scales::hue_pal()(length(ms_n))

# good_ms <- list()

# for (mn in ms_n) {
#   fit <- ms[[mn]]
#   conv <- as.character(fit$opt$convergence)

#   if (conv == "0") {
#     good_ms[[mn]] <- fit
#   }

#   cat(mn, "-> convergence:", conv, "\n")
# }

# ms <- good_ms
# ms_n <- names(ms)

```


# Plotspict compare

```{r plotspictgeneral}
tryCatch(
  {
    plotspict.compare(ms, col = gg_cols)
    plotspict.compare(ms, CI = 0, col = gg_cols)
  },
  error = function(e) {
    message("\n An error occurred:\n", e$message)
  }
)
```

## Biomass

```{r biomass}
tryCatch(
  {
    plotspict.compare(ms, varname = "B", plot.legend = 2, col = gg_cols)
    plotspict.compare(ms, varname = "B", CI = 0, col = gg_cols)
    plotspict.compare(ms, varname = "BBmsy", plot.legend = 2, col = gg_cols)
    plotspict.compare(ms, varname = "BBmsy", CI = 0, col = gg_cols)
  },
  error = function(e) {
    message("\n An error occurred:\n", e$message)
  }
)
```

## Fishing mortality

```{r fmortality}
tryCatch(
  {
    plotspict.compare(ms, varname = "F", col = gg_cols)
    plotspict.compare(ms, varname = "F", CI = 0, col = gg_cols)
    plotspict.compare(ms, varname = "FFmsy", col = gg_cols)
    plotspict.compare(ms, varname = "FFmsy", CI = 0, col = gg_cols)
  },
  error = function(e) {
    message("\n An error occurred:\n", e$message)
  }
)
```

## Catch and Production

```{r catchandprod}
tryCatch(
  {
    plotspict.compare(ms, varname = "C", col = gg_cols)
    plotspict.compare(ms, varname = "C", CI = 0, col = gg_cols)
    plotspict.compare(ms, varname = "P", col = gg_cols)
    plotspict.compare(ms, varname = "P", CI = 0, col = gg_cols)
  },
  error = function(e) {
    message("\n An error occurred:\n", e$message)
  }
)
```

# Reference points

## MSY

```{r msy}
rp_vars <- c("logMSY")

comp_plot(ms = ms, variables = rp_vars)

```

## Bmsy

```{r bmsy}
rp_vars <- c('logBmsy')

comp_plot(ms = ms, variables = rp_vars)
```

## Fmsy

```{r fmsy}
rp_vars <- c('logFmsy')

comp_plot(ms = ms, variables = rp_vars)

```

# State of the stock

## Final year biomass

```{r bbmsy}
rp_vars <- c("logBlBmsy")

comp_plot(ms = ms, variables = rp_vars)
```

```{r bl}
rp_vars <- c("logBl")

comp_plot(ms = ms, variables = rp_vars)
```

## Final year fishing mortality

```{r ffmsy}
rp_vars <- c("logFlFmsy")
comp_plot(ms = ms, variables = rp_vars)
```

```{r fl}
rp_vars <- c("logFl")
comp_plot(ms = ms, variables = rp_vars)
```

# Important parameters

## BKfrac

```{r bkfrac}
rp_vars <- c("logbkfrac")
comp_plot(ms = ms, variables = rp_vars)
```

## n

```{r logn}
rp_vars <- c("logn")
comp_plot(ms = ms, variables = rp_vars)
```

## r

```{r logr}
rp_vars <- c("logr")
comp_plot(ms = ms, variables = rp_vars)
```

## K

```{r logK}
rp_vars <- c("logK")
comp_plot(ms = ms, variables = rp_vars)
```

# Standard deviation values

## sdc

```{r sdc}
sd_values <- c("logsdc")
comp_plot(ms = ms, variables = sd_values)
```

## sdi

```{r sdi}
sd_values <- c("logsdi")
comp_plot(ms = ms, variables = sd_values)
```

## sdb

```{r sdb}
sd_values <- c("logsdb")
comp_plot(ms = ms, variables = sd_values)
```

## sdf

```{r sdf}
sd_values <- c("logsdf")
comp_plot(ms = ms, variables = sd_values)

```

## alpha

```{r alpha}
sd_values <- c("logalpha")
comp_plot(ms = ms, variables = sd_values)
```

## beta

```{r beta}
sd_values <- c("logbeta")
comp_plot(ms = ms, variables = sd_values)
```

# Catch observed vs fitted

Observed catches are extracted from the first model in the list.

```{r obscatch}
comp_plot2(ms = ms, variables = c("logCpred"))
```

# Index observed vs fitted

Observed index is extracted from the first model in the list.

```{r obsindex}
comp_plot2(ms = ms, variables = c("logIpred"))
```


