---
format: 
  html:
    embed-resources: true
    theme: cosmo
    toc: true
    toc-depth: 3
    toc-expand: true
execute:
  echo: false
  warning: false
  message: false
params:
  model: NULL
  run_description: NULL
  run_inp: NULL
  run_priors: NULL
  run_sdfacs: NULL
  run_ini_trials: 10
  run_retro_chunk: false
  retro_years: 5  
  hindcast_years: 5
  run_manage_chunk: true
  save_large_files: true
---

```{r knit-setup, eval = TRUE, include = FALSE, cache = FALSE}

knitr::opts_knit$set(root.dir = '../../')

knitr::knit_hooks$set(timeit = local({
  now = NULL
  function(before, options) {
    if (before) {
      now <<- Sys.time()
    } else {
      res = round(difftime(Sys.time(), now, units = "mins"), 1)
      now <<- NULL
      # use options$label if you want the chunk label as well
      print(paste('Time:', as.character(res), "min"))
    }
  }})
)
```


```{r params}
# Functions and packages
source("src/spict_functions.R")
source("src/exploration/additional_spict_funcs.R")
source("src/ices_plots.R")

# Access parameters
model <- params$model
description <- params$run_description
inp_new <- params$run_inp
priors <- params$run_priors
sdfacs <- params$run_sdfacs

ini_trials <- params$run_ini_trials
nretroyears <- params$retro_years
nhindcastyears <- params$hindcast_years
save_large_files <- params$save_large_files

cat("Model:", model, "\n")
cat("Description:", description, "\n")
```

<details>
<summary>Unfold to see R package versions and system information used to generate this document</summary>
```{r}
#| label: sys-info
sessionInfo()
```
</details>

```{r fitspict}
inp <- check.inp(inp_new, verbose = TRUE)

for (nm in names(priors)) {
  inp$priors[[nm]] <- priors[[nm]]
}

inp$stdevfacC <- sdfacs$stdevfacC
inp$stdevfacI <- sdfacs$stdevfacI

fitspict_crash <- FALSE

res <- tryCatch(
  {
    fit.spict(inp) # your original call
  },
  error = function(e) {
    message("fit.spict() failed: ", conditionMessage(e))
    fitspict_crash <<- TRUE
    list(opt = list(convergence = 1)) # return a sentinel so downstream code can check
  }
)

if (save_large_files) {
  dest <- paste0("data/model_output/saved_models/", "res_", model, ".rds")
  if (!dir.exists(dirname(dest))) {
    dir.create(dirname(dest), recursive = TRUE)
  }
  saveRDS(res, file = dest, compress = "xz")
}
# dev.off()

if (fitspict_crash) {
  knitr::knit_exit()
}
```

# Summary and  parameter correlation matrix

```{r summary}
#| echo: true
summary(res)
all(is.finite(res$sd))
cov2cor(res$cov.fixed)
```

# Magnitude of uncertainty and initial values sensitivity

```{r initialvalues}
#| echo: true
calc.om(res)
check.ini(inp, ntrials = ini_trials)
```

# General plots

```{r generalplots}
plot(res)
```

## Biomass

```{r biomass}
tryCatch(
  {
    plotspict.bbmsy(res)
  },
  error = function(e) {
    message("Plot skipped: ", e$message)
  }
)

tryCatch(
  {
    plotspict.biomass(res)
  },
  error = function(e) {
    message("Plot skipped: ", e$message)
  }
)
```

## Catch and F

```{r catch}
tryCatch(
  {
    plotspict.catch(res)
  },
  error = function(e) {
    message("Plot skipped: ", e$message)
  }
)

tryCatch(
  {
    plotspict.f(res)
  },
  error = function(e) {
    message("Plot skipped: ", e$message)
  }
)

tryCatch(
  {
    plotspict.ffmsy(res)
  },
  error = function(e) {
    message("Plot skipped: ", e$message)
  }
)
```

## Kobe and Years to Bmsy

```{r kobe}
tryCatch(
  {
    plotspict.fb(res)
  },
  error = function(e) {
    message("Plot skipped: ", e$message)
  }
)

tryCatch(
  {
    plotspict.tc(res)
  },
  error = function(e) {
    message("Plot skipped: ", e$message)
  }
)


```

## Production curve and priors

```{r priors}
tryCatch(
  {
    plotspict.production(res)
  },
  error = function(e) {
    message("Plot skipped: ", e$message)
  }
)


tryCatch(
  {
    plotspict.priors(res)
  },
  error = function(e) {
    message("Plot skipped: ", e$message)
  }
)
```

# Catch observed vs fitted

```{r obscatch}

tryCatch(
  {
    comp_plot2(ms = c("res"), variables = c("logCpred"))
  },
  error = function(e) {
    message("Plot skipped: ", e$message)
  }
)

```

# Index observed vs fitted

```{r obsindex}

tryCatch(
  {
    comp_plot2(ms = c("res"), variables = c("logIpred"))
  },
  error = function(e) {
    message("Plot skipped: ", e$message)
  }
)
```

# OSA residuals

```{r osa, fig.height = 10}

tryCatch(
  {
    res <- calc.osa.resid(res)
    plotspict.diagnostic(res)
  },
  error = function(e) {
    message("Plot skipped: ", e$message)
  }
)

```

# Process residuals

```{r process, fig.height = 10}

tryCatch(
  {
    res <- calc.process.resid(res)
    plotspict.diagnostic.process(res)
  },
  error = function(e) {
    message("Plot skipped: ", e$message)
  }
)

```

# Retros and hindcasting

```{r retros, eval=params$run_retro_chunk}

tryCatch(
  {
    res <- retro(res, nretroyear = nretroyears, mc.cores = 1)
    plotspict.retro(res)
    plotspict.retro.fixed(res)
  },
  error = function(e) {
    message("Plot skipped: ", e$message)
  }
)

tryCatch(
  {
    res <- hindcast(res, npeels = nhindcastyears)
    plotspict.hindcast(res)
  },
  error = function(e) {
    message("Plot skipped: ", e$message)
  }
)


```

# Management scenarios

```{r manage, eval=params$run_manage_chunk}

tryCatch(
  {
    TACyear <- res$inp$timeC[length(res$inp$timeC)] + 2

    man <- manage(
      res,
      scenarios = c("currentF", "Fmsy", "noF", "ices"),
      maninterval = c(TACyear, TACyear + 1),
      maneval = TACyear + 1
    )

    # man <- add.man.scenario(
    #   man,
    #   scenarioTitle = "15th percentile",
    #   maninterval = c(TACyear, TACyear + 1),
    #   maneval = TACyear + 1,
    #   fractiles = list(catch = 0.15),
    #   breakpointB = 0.5,
    #   safeguardB = list(limitB = 0.3, prob = 0.95)
    # )

    manOutput <- sumspict.manage(man, include.unc = TRUE)

    risk <- spictRisk(man, bmsyfrac = 0.5, years = c(TACyear - 1, TACyear)) # 0.5 = Btrigger

    plotspict.hcr(man)

    manTable <- bind_cols(
      manOutput$est,
      manOutput$unc,
      risk %>%
        mutate(across(BbelowBmsy:FaboveFlim, ~ . * 100)) %>% # change to percent?
        pivot_wider(
          id_cols = Scenario,
          values_from = BbelowBmsy:FaboveFlim,
          names_from = Year
        )
    ) %>%
      mutate(Scenario = rownames(manOutput$est)) %>%
      relocate(Scenario)
  },
  error = function(e) {
    message("\n An error occurred in the management chunk:\n", e$message)
  }
)
```

# SPiCT summary

```{r spict-summary}
tryCatch(
  {
    spict_summary <- list(
      summary = data.frame(
        year = as.numeric(row.names(get.par("logBBmsy", res, exp = TRUE))),
        BBmsy = as.data.frame(get.par("logBBmsy", res, exp = FALSE)),
        FFmsy = as.data.frame(get.par("logFFmsy", res, exp = FALSE)),
        K = as.data.frame(get.par("logK", res, exp = FALSE)),
        r = as.data.frame(get.par("logr", res, exp = FALSE)),
        n = as.data.frame(get.par("logn", res, exp = FALSE)),
        sdi1 = as.data.frame(get.par("logsdi", res, exp = FALSE))[1, ],
        sdi2 = as.data.frame(get.par("logsdi", res, exp = FALSE))[2, ],
        sdc = as.data.frame(get.par("logsdc", res, exp = FALSE)),
        BKfrac = as.data.frame(get.par("logbkfrac", res, exp = FALSE))
      ) %>%
        left_join(
          data.frame(year = inp$timeC, total_catch = inp$obsC)
        ) %>%
        full_join(
          data.frame(
            year = min(man$inp$timeC):man$inp$timepredc,
            Catch_pred = as.data.frame(get.par("logCpred", res, exp = TRUE))
          )
        ) %>%
        full_join(
          data.frame(
            year = inp$timeI[[1]],
            index = inp$obsI[[1]]
          )
        ),
      refpoints = sumspict.drefpoints(res),
      state = sumspict.states(res),
      pars = as.data.frame(sumspict.parest(res)),
      manTable = manTable,
      priors = res$inp$priors,
      assessment_year = TACyear - 1,
      tac_year = TACyear
    )

    dest <- paste0(
      "data/model_output/spict_summaries/",
      "sum_",
      model,
      ".rds"
    )
    if (!dir.exists(dirname(dest))) {
      dir.create(dirname(dest), recursive = TRUE)
    }
    saveRDS(spict_summary, file = dest, compress = "xz")
  },
  error = function(e) {
    message("\n An error occurred in the SPiCT summary chunk:\n", e$message)
  }
)
```

```{r}
#| label: fig-summary-plot
#| fig-cap: "ICES assessment summary plot."
tryCatch(
  {
    summary_plot(spict_summary)
  },
  error = function(e) {
    message("\n An error occurred in the ICES summary plot chunk:\n", e$message)
  }
)
```






