---
subtitle: "Assessment report"
date: today
published-title: "Version"
lang: {{LANGUAGE}}
bibliography: ../assets/references.bib
csl: ../assets/ices_jms.csl
output-file: "{{PROJECT_SLUG}}-assessment-report"
params:
  assessment_year: {{ASSESSMENT_YEAR}}   # Year the assessment is carried out
  advice_year: {{ADVICE_YEAR}}           # Year advice is given for
  prev_advice_year: {{PREV_ADVICE_YEAR}} # Year advice was last given
  chapter: "X"                           # The chapter number the working group assigned
format:
  html:
    self-contained: true
    toc: true
    toc-depth: 3
    fig-width: {{FIG_WIDTH_DOUBLE}}
    fig-height: 4
  docx:
    # Pick the body this chapter reports to. All three templates are in docs/assets/:
    #   ../assets/jrn_afwg_report_template.docx          — JRN-AFWG
    #   ../assets/ices_scientific_reports_template.docx  — ICES Scientific Reports
    #   ../assets/nettrapport_template.docx              — internal IMR
    # The groups reissue their templates; confirm the shipped one is still current.
    reference-doc: ../assets/jrn_afwg_report_template.docx
    number-sections: false
    fig-width: {{FIG_WIDTH_DOUBLE}}
    fig-height: 4
    fig-dpi: 300
    fig-align: left
prefer-html: true
crossref:
  chapters: true
execute:
  echo: false
  warning: false
  message: false
editor_options:
  chunk_output_type: console
---

<!--
This is a CHAPTER of a working-group report, so it carries no YAML title: the chapter heading
below is the title, and the group's template supplies the styles.

Float numbering is the group's, not yours — "Table 6.8", "Figure 6.23" — so `number-sections`
is false, the assigned number is written into the caption text, and the label slug mirrors it.
Never renumber a float to match your prose; other chapters cross-reference the group's number.
All floats sit at the end, under "Tables and figures", in the group's order.

This chapter reports the SELECTED SPiCT run. It does not refit. Read the installed
`academic-assessment-report` skill and the pack's knowledge/advice.md before editing.
-->

```{r setup}
#| include: false
knitr::opts_knit$set(root.dir = here::here())
source(here::here("R", "0_setup.R"))
source(here::here("R", "report_helpers.R"))
source(here::here("R", "advice_tables.R"))
source(here::here("R", "ices_plots.R"))
```

```{r assessment-values}
#| include: false
# Every headline number the chapter quotes, derived once from the selected run. A chapter is
# rewritten each year against a new model run, and a stale number is this document type's
# classic error.
assessment_year  <- params$assessment_year
advice_year      <- params$advice_year
prev_advice_year <- params$prev_advice_year
ch <- params$chapter

summary_path <- file.path(
  output_dir,
  paste0(cfg$STOCK_SLUG, "_spict_summary_", assessment_year, ".rds")
)
if (!file.exists(summary_path)) {
  stop(
    "No assessment summary for ", assessment_year, " at ", summary_path,
    ". Render docs/data-report/spict-assessment/ first.",
    call. = FALSE
  )
}
spict_summary <- readRDS(summary_path)

catches  <- readRDS(file.path(output_dir, paste0(cfg$STOCK_SLUG, "_catches.rds")))
landings <- readRDS(file.path(output_dir, paste0(cfg$STOCK_SLUG, "_landings.rds")))

first_data_year <- min(catches$year)
last_data_year  <- max(catches$year)

index_years <- spict_summary$summary |>
  dplyr::filter(!is.na(index)) |>
  dplyr::pull(year) |>
  floor() |>
  range()

state_df <- as.data.frame(spict_summary$state)
state_df$Quantity <- rownames(state_df)
status_quo_F <- state_df$estimate[grepl("/Fmsy$", state_df$Quantity)]
status_quo_B <- state_df$estimate[grepl("/Bmsy$", state_df$Quantity)]

blim     <- cfg$BLIM_BMSY %||% 0.3
btrigger <- cfg$BTRIGGER_BMSY %||% 0.5

f_status <- if (status_quo_F > 1) "above" else "below"
b_status <- dplyr::case_when(
  status_quo_B < blim ~ "below B~lim~",
  status_quo_B < btrigger ~ "below MSY B~trigger~ but above B~lim~",
  .default = "above MSY B~trigger~"
)

advised_catch <- spict_summary$manTable |>
  dplyr::filter(stringr::str_detect(Scenario, "ICES advice rule")) |>
  dplyr::pull(C) |>
  round()

checks <- spict_summary$diagnostics
failed <- if (is.null(checks)) character() else checks$Check[!checks$Passed]
```

# {{STOCK_NAME_SENTENCE}} (*{{STOCK_LATIN}}*) in ICES subareas {{ICES_AREAS}} — exploratory SPiCT assessment

::: {.callout-warning}
This chapter reports an **exploratory** SPiCT assessment. It supplements, and does not replace, the official {{WORKING_GROUP}} assessment, which uses `r cfg$OFFICIAL_ASSESSMENT`. Do not remove this notice — see the pack's `knowledge/constraints.md`.
:::

## Status of the fisheries

Total catches in `r last_data_year` were `r fmt(catches$total[catches$year == last_data_year])` t, against a series mean of `r fmt(mean(catches$total))` t over `r first_data_year`–`r last_data_year` (Table `r ch`.1, Figure `r ch`.1). The most recent year is preliminary.

[VERIFY — describe the fleets, the gears, and the management measures in force in the most recent years. Name what changed since the last assessment.]

## Data used in the assessment

### Catch data

The catch series covers `r first_data_year`–`r last_data_year` and is compiled from the sources recorded in `ai/memory/catch-data-sources.md`. Catches are total catches in tonnes.

[VERIFY — state what changed in the catch data since last year's assessment and why. A revision to a historical year is more consequential than a new year and is easy to leave unmentioned.]

### Survey data

The assessment is driven by the `r tolower(cfg$INDEX_NAME)`, covering `r index_years[1]`–`r index_years[2]`. The index is **relative**, not absolute: SPiCT estimates the catchability that links it to biomass, and only its shape over time carries information.

[VERIFY — name the surveys, the gear, and the area the index covers, and state what effort denominator it uses. See academic-style/references/ecology-fisheries.md.]

### Biological data

SPiCT uses no age or length data. Life-history information enters the assessment only through the prior on the intrinsic growth rate — see @tbl-priors-chapter and `ai/memory/priors.md`.

## Assessment

### Model settings

The model is a Schaefer surplus-production model [@pedersen2017] fitted with spict `r spict_summary$spict_version`. The shape parameter is fixed at the Schaefer value; the index is scaled to its own mean and placed at `r cfg$INDEX_TIMING` of the year; catch observation errors are downweighted before `r cfg$STDEV_HIGH_YEAR` through a linear ramp.

The full model configuration, the priors, and the code that produced them are in the assessment data report (`docs/data-report/spict-assessment/`), which this chapter does not repeat.

### Model diagnostics

`r if (length(failed) == 0) "The fit passed every acceptance check." else paste0("The fit did not pass ", spell_number(length(failed)), " of the acceptance checks: ", list_values(failed), ".")` The checks and their criteria are in Table `r ch`.2.

[VERIFY — where a check failed, say by how much and what it means for the assessment's reliability. This section is what reviewers read first; write it honestly.]

### Assessment results

Exploitable biomass at the end of `r last_data_year` was estimated `r b_status` (B/B~MSY~ = `r round_report(status_quo_B)`), and fishing pressure `r f_status` F~MSY~ (F/F~MSY~ = `r round_report(status_quo_F)`) (Figure `r ch`.2, Table `r ch`.3).

## Comments to the assessment

[VERIFY — what the assessment does not capture, and how much confidence it deserves. A surplus-production model compresses recruitment, growth, and natural mortality into one production function, so a stock whose productivity has changed over the series is represented only approximately. Say whether that matters here.]

## Biological reference points

SPiCT provides reference points on the **relative** scale only. MSY B~trigger~ and B~lim~ are conventions supplied by the advice framework, set at B/B~MSY~ = `r btrigger` and `r blim` following the ICES standard for SPiCT stocks; F~MSY~ is estimated by the model and changes when the assessment is updated (Table `r ch`.4).

[VERIFY — where this stock has absolute reference points from another assessment, state them here with their own source named. Do not imply the SPiCT model produced them.]

## Management advice

Under the `r cfg$ADVICE_FRAMEWORK`, catches in `r advice_year` should be no more than `r fmt(advised_catch)` t (Table `r ch`.5). The full set of catch scenarios and their risk probabilities is in the assessment data report and on the advice sheet.

## Future development of the assessment

[VERIFY — be specific enough that this list can become the next benchmark's issue list. Candidates: recalibrating the priors from this stock's life history rather than a congener's; revisiting the catch-uncertainty breakpoints; testing an alternative index variant; and any acceptance check that failed this year.]

## Software and reproducibility

The assessment was run in `r R.version.string` [@rcoreteam] with spict `r spict_summary$spict_version` [@pedersen2017]. This chapter was compiled with Quarto [@quarto] and rendered by knitr [@knitr], and is reproducible from the saved model output.

This document and the associated analyses were created with researcher-supervised generative AI (<!-- EXACT MODEL NAMES AND ROLES, CONFIRMED BY THE RESEARCHER -->). The authors specified and checked the assessment, and reviewed, edited, and approved all AI-assisted content, for which they take full responsibility.

## References

::: {#refs}
:::

{{< pagebreak >}}

## Tables and figures

<!--
Every float goes here, in the working group's order, with the group's assigned number written
into the caption. The `params$chapter` value stamps the chapter number so a renumbering by the
group is one parameter change rather than an edit to every caption.
-->

```{r}
#| label: tbl-catch-history-chapter
#| tbl-cap: !expr 'paste0("Table ", ch, ".1. Reported catches by nation, in tonnes. The most recent year is preliminary.")'
make_table(landings)
```

```{r}
#| label: tbl-diagnostics-chapter
#| tbl-cap: !expr 'paste0("Table ", ch, ".2. Acceptance checks applied to the assessment, their criteria, and the verdict.")'
if (!is.null(checks)) {
  make_table(dplyr::mutate(checks, Passed = ifelse(Passed, "Yes", "No")))
}
```

```{r}
#| label: tbl-states-chapter
#| tbl-cap: !expr 'paste0("Table ", ch, ".3. Estimated stock status at the end of ", last_data_year, ", with 95 % confidence intervals.")'
spict_summary$state |>
  as.data.frame() |>
  tibble::rownames_to_column("Quantity") |>
  dplyr::mutate(dplyr::across(where(is.numeric), round_report)) |>
  make_table()
```

```{r}
#| label: tbl-priors-chapter
#| tbl-cap: !expr 'paste0("Table ", ch, ".4. Priors used in the assessment, and the reference points they imply.")'
if (!is.null(spict_summary$srefpoints)) {
  spict_summary$srefpoints |>
    as.data.frame() |>
    tibble::rownames_to_column("Reference point") |>
    dplyr::mutate(dplyr::across(where(is.numeric), round_report)) |>
    make_table()
}
```

```{r}
#| label: tbl-scenarios-chapter
#| tbl-cap: !expr 'paste0("Table ", ch, ".5. Catch scenarios for ", advice_year, ". Catches in tonnes.")'
spict_summary$manTable |>
  dplyr::mutate(dplyr::across(where(is.numeric), round_report)) |>
  make_table()
```

```{r}
#| label: fig-catches-chapter
#| fig-cap: !expr 'paste0("Figure ", ch, ".1. Reported catches by nation, ", first_data_year, "-", last_data_year, ".")'
#| fig-height: 4
landings |>
  tidyr::pivot_longer(-year, values_drop_na = TRUE) |>
  ggplot(aes(year, value / 1000, fill = name)) +
  geom_col() +
  scale_y_continuous(expand = expansion(c(0, 0.02))) +
  labs(x = "Year", y = "Catch (kt)", fill = NULL)
```

```{r}
#| label: fig-summary-chapter
#| fig-cap: !expr 'paste0("Figure ", ch, ".2. Stock summary: total catches, relative fishing pressure, and relative exploitable biomass, with 95 % confidence intervals and the reference points.")'
#| fig-height: 6
summary_plot(spict_summary)
```
